# Adults

This section describes environmental attributes associated with and responses during the adult life stage (ocean harvest, migration, spawning)

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
source("functions.R")
```

## Habitat Attributes 
1. Hatchery Influence (Proportion of hatchery return)

2. Hatchery Pathogens/Disease

3. In-River Pathogens/Disease

4. Spawning Habitat Capacity (SIT model)

## Environmental Drivers {#wq}

1. Water Temperature 

Water temperatures were warmer than average in 2020 (Figure \@ref(fig:historicalwtemp-fig)).
 
```{r BSFwtemp-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Sacramento River Water Temperature at Ball's Ferry Bridge TCP (BSF)."}
temp_data <- readRDS("data_raw/temp_cdec_2011-2023.rdsxz")
temp_BSF <- temp_data %>%
  filter(station == "BSF",
         year == 2021,
         month>3 & month < 10) %>%
  group_by(date) %>%
  summarize(Temperature = mean(Temperature, na.rm = TRUE))

ggplot(temp_BSF) + 
  geom_line(aes(date, Temperature), color = "steelblue") +
  geom_hline(yintercept  = 56, linetype = "dashed", color = "gray50") + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  labs(y = "Water Temperature (°C)") +
  theme_plots 

```


```{r historicalwtemp-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Historical Comparison of Sacramento River Water Temperature at Clear Creek (CCR) and Balls Ferry Bridge (BSF)."}
temp_years <- temp_data %>%
  filter(date<as.Date("2022-01-01")) %>%
  group_by(date, date2, year, month, wy, station) %>%
  summarize(Temperature = mean(Temperature, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(fyear = factor(year)) %>%
  dplyr::select(station, date2, Temperature, fyear)

temp_avg <- temp_data %>%
  filter(date<as.Date("2022-01-01")) %>%
  group_by(station, date2) %>%
  summarize(Temperature = mean(Temperature, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(fyear = "mean")

temp_all <- rbind(temp_years, temp_avg) %>%
  filter(fyear %in% c("mean", "2011", "2020", "2017")) %>%
  rename(doy = date2)

ggplot(temp_all) + geom_line(aes(doy, Temperature, color = fyear)) +
  facet_wrap(~station, nrow = 2) + 
  scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  labs(y = "Water Temperature (°C)") +
  theme_plots 
```

## Biological Response

1. Ocean Harvest Rates (PFMC)

2. Adults to Hatchery (GrandTab)

3. Estimated Total Mainstem In-River Spawners of Natural and Hatchery Origin (GrandTab)

* Downstream RBDD
* Upstream RBDD
* Clear Creek
* Battle Creek

4. Adult Condition (Carcass Surveys)

* Male Fork Lengths (Histogram)
* Female Fork Lengths (Histogram)
* Age Distribution
* Thiamine Deficiency
* Pre-spawn mortality (in-text current year and 10-yr average, compare with other years)

5. Spawn Timing (Carcass Surveys)

* Percent spawning by week - line plot of percent of carcasses by week (current year, 10 year and 20 year average)
* Peak spawning week - line plot of peak spawning week by year (annual, rolling 5-year avg, 10-year avg)

6. Number of Winter-Run Chinook Salmon Redds (aerial redd surveys, Calfish)

* line plot of count by year with average horizontal line 

7. Distribution of Winter-Run Chinook Salmon Redds - location of redds (aerial redd surveys, Calfish)

* map of locations 
* bar plot of percent redds by location (historical and this year)
* bar plot of female spawner carcasses by location

8. Hatchery Fecundity (JPE Letters)

* in text, comparison with previous 10 years

9. Hatchery Influence (Hatchery report?)

* in text percentage of hatchery fish/natural spawning pop

10. Cohort Replacement Rate (GrandTab)

* line plot of CRR by year 

