# Egg to Fry Emergence

This section describes environmental attributes associated with and responses during the egg-to-fry life stage.

```{r setup2, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```


```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)
library(readr)
library(here)
library(scales)
library(rvest)

library(kableExtra)
library(flextable)
library(CDECRetrieve)
source("functions.R")
source("parameters.R")
```

## Environmental Drivers

### Storage and Flow

#### Shasta Storage 

-   See \@ref(shasta-storage) for summary of storage conditions.

#### Flow Conditions on the Upper Sacramento River

```{r KWKBNDflowegg}
flow_kwk_bnd_monthly_egg <- readRDS(paste0("data_raw/flow_kwk_bnd_monthly_", year(start), "-", year(end), ".rds")) %>%
  filter(!month %in% c("January", "February", "March", "April", "December")) %>%
  mutate(station = factor(station, levels = c("KWK", "BND"))) %>%
  select(Year=year, station, month, everything()) %>%
  arrange(station)

flow_kwk_bnd_monthly_egg_t <- flow_kwk_bnd_monthly_egg

colnames(flow_kwk_bnd_monthly_egg_t) <- stringr::str_to_title(colnames(flow_kwk_bnd_monthly_egg_t))

kable(flow_kwk_bnd_monthly_egg_t,
      label = NA,
      vline = "",
      caption = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Sacramento River at Keswick (KWK) and Sacramento River at Bend Bridge (BND) between May and November", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(7,extra_css = "border-bottom: 1px solid;")


# flextable(flow_kwk_bnd_monthly_egg)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = 7, part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "Year", big.mark = "") %>%
#   set_header_labels(month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)")
```


```{r echo = FALSE}
monthly_kwk_egg <- flow_kwk_bnd_monthly_egg %>% filter(station == "KWK")
max_flow_kwk_egg <- max(monthly_kwk_egg$max)
max_mean_flow_kwk_egg <- max(monthly_kwk_egg$mean)
max_flow_kwk_month_egg <- monthly_kwk_egg %>% filter(max == max_flow_kwk_egg) %>% select(month)
max_mean_flow_kwk_month_egg <- monthly_kwk_egg %>% filter(mean == max_mean_flow_kwk_egg) %>% select(month)

monthly_bnd_egg <- flow_kwk_bnd_monthly_egg %>% filter(station == "BND")
max_flow_bnd_egg <- max(monthly_bnd_egg$max)
max_mean_flow_bnd_egg <- max(monthly_bnd_egg$mean)
max_flow_bnd_month_egg <- monthly_bnd_egg %>% filter(max == max_flow_bnd_egg) %>% select(month)
max_mean_flow_bnd_month_egg <- monthly_bnd_egg %>% filter(mean == max_mean_flow_bnd_egg) %>% select(month)
```

-   **Keswick:** Peak flows were **`r max_flow_kwk_egg`** cfs and occurred in **`r max_flow_kwk_month_egg[1]`**. The highest mean flows were **`r max_mean_flow_kwk_egg`** cfs and occurred in **`r max_mean_flow_kwk_month_egg`**.
-   **Bend Bridge:** Peak flows were **`r max_flow_bnd_egg`** cfs and occurred in **`r max_flow_bnd_month_egg[1]`**. The highest mean flows were **`r max_mean_flow_bnd_egg`** cfs and occurred in **`r max_mean_flow_bnd_month_egg`**.

### Water Temperature on the Upper Sacramento River

- See \@ref(temp-thresholds) for discussion around temperature threshold analysis.

### Dissolved Oxygen Conditions on the Upper Sacramento River

```{r CCRKWKdoegg-tab}

do_kwk_ccr_monthly_egg <- readRDS(paste0("data_raw/do_KWK_CCR_monthly_", year(start), "-", year(end), ".rds"))%>%
  filter(!month %in% c("January", "February", "March", "April", "December")) %>%
  mutate(station = factor(station, levels = c("KWK", "CCR"))) %>%
  select(Year = year, station, month, everything()) %>%
  arrange(station)

do_kwk_ccr_monthly_egg_t <- do_kwk_ccr_monthly_egg

colnames(do_kwk_ccr_monthly_egg_t) <- stringr::str_to_title(colnames(do_kwk_ccr_monthly_egg_t))

kable(do_kwk_ccr_monthly_egg_t,
      label = NA,
      vline = "",
      caption = paste("Mean, Maximum, Minimum Monthly Dissolved Oxygen (mg/L) at Sacramento River at Keswick (KWK) and Sacramento River upstream from Confluence with Clear Creek (CCR) between May and November", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(7,extra_css = "border-bottom: 1px solid;")

# flextable(do_kwk_ccr_monthly_egg)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = 7, part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "Year", big.mark = "") %>%
#   set_header_labels(month = "Month", station = "Station", mean = "Mean (mg/L)", max = "Max (mg/L)", min =  "Min (mg/L)")
```

```{r echo = FALSE}
monthly_kwk_egg <- do_kwk_ccr_monthly_egg %>% filter(station == "KWK")
min_do_kwk_egg <- min(monthly_kwk_egg$min)
min_mean_do_kwk_egg <- min(monthly_kwk_egg$mean)
min_do_kwk_egg_month <- monthly_kwk_egg %>% filter(min == min_do_kwk_egg) %>% select(month)
min_mean_do_kwk_egg_month <- monthly_kwk_egg %>% filter(mean == min_mean_do_kwk_egg) %>% select(month)

monthly_ccr_egg <- do_kwk_ccr_monthly_egg %>% filter(station == "CCR")
min_do_ccr_egg <- min(monthly_ccr_egg$min)
min_mean_do_ccr_egg <- min(monthly_ccr_egg$mean)
min_do_ccr_egg_month <- monthly_ccr_egg %>% filter(min == min_do_ccr_egg) %>% select(month)
min_mean_do_ccr_egg_month <- monthly_ccr_egg %>% filter(mean == min_mean_do_ccr_egg) %>% select(month)
```

**Summary**

-   **Keswick:** Minimum dissolved oxygen was **`r min_do_kwk_egg`** mg/L and occurred in **`r min_do_kwk_egg_month[1]`**. The lowest mean dissolved oxygen was **`r min_mean_do_kwk_egg`** mg/L and occurred in **`r min_mean_do_kwk_egg_month`**.
-   **Clear Creek:** Minimum dissolved oxygen was **`r min_do_ccr_egg`** mg/L and occurred in **`r min_do_ccr_egg_month[1]`**. The lowest mean dissolved oxygen was **`r min_mean_do_ccr_egg`** mg/L and occurred in **`r min_mean_do_ccr_egg_month`**.


### Air Temperature 

```{r KRDDatemp-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Air Temperature (deg F) at Redding Municipal Airport from May",report_year, "through November", report_year, "and maximum and minimum temperatures since 2003"), fig.width = 8, fig.height = 4.5}
airtemp_krdd_allyears <- read_csv(here("data_raw", paste0("atemp_daily_krdd_allyears.csv"))) %>%
  select(-date) %>%
  filter(year == report_year) %>%
  filter(month_num>5 & month_num<12)

min <- airtemp_krdd_allyears %>%
  filter(var == "min") %>%
  rename(min = atemp)
max <- airtemp_krdd_allyears %>%
  filter(var == "max") %>%
  rename(max = atemp)
fill <- left_join(min %>% select(date2, min), max %>%select(date2, max))

plotly::ggplotly(ggplot() + 
  geom_line(data = airtemp_krdd_allyears,aes(date2, atemp, linetype = var)) +
  geom_line(data = airtemp_krdd_allyears %>%filter(var!="mean"),aes(date2, extreme, linetype = var), color = "brown") +
  geom_ribbon(data = fill, aes(x = date2, ymin= min, ymax = max), fill = "steelblue4", alpha = 0.5) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  # scale_color_manual(values = c("black", "steelblue")) +
  # scale_linetype_manual(values = c("dashed", "solid")) +
  labs(y = "Air Temperature (degrees F)") +
  theme_plots +
    theme(legend.title = element_blank()))
```


## Biological Response

### Egg to Fry Survival


```{r}
jpe_data <- read_csv("data_raw/jpe_data.csv")
eggs <- jpe_data %>% filter(component == "Total eggs") %>% filter(brood_year <= report_year)
tenyear = eggs %>% filter(brood_year > report_year-10 & brood_year<= report_year)
twentyyear = eggs %>% filter(brood_year > report_year-20 & brood_year<= report_year)
```

```{r}
jpe <- url_jpe <- "https://www.cbr.washington.edu/sacramento/data/jpe_data.html"
jpi <- url_jpe %>%
  read_html() %>%
  html_nodes(xpath = '/html/body/div[2]/div[12]/table') %>%
  html_table() %>%
  bind_rows() %>%
  janitor::clean_names() %>%
  filter(row_number() <= n()-1,
         !brood_year %in% c(2003, 2004)) %>%
  mutate(brood_year = as.numeric(brood_year),
         value = stringr::str_replace(value, ",", ""),
         jpi = as.numeric(value))
jpi_tenyear <- jpi %>% filter(brood_year >= report_year-10 & brood_year <=report_year) %>%
  mutate(value = as.numeric(value))
```

```{r}
jpi <- read.csv("data_raw/JPI_2002_2023.csv") %>%
  filter(BY <= report_year) %>%
  rename(JPI = Fry.Equivalent.JPI,
         ETF_Survival = ETF.Survival.Rate....) %>%
  select(BY, JPI, ETF_Survival) %>%
  mutate(JPI = JPI/1000000,
         JPI_lab = round(JPI, 2),
         ETF_Survival_lab = round(ETF_Survival)) %>%
  mutate(BY_fac = factor(BY))

tdm <- read.csv("data_raw/ETF_TDM_2002_2023.csv") %>%
  mutate(unexplained_mortality = 100-ETF_Survival-TDM_NOAA_percent) %>%
  rename(ETF_survival = ETF_Survival) %>%
  filter(Brood.Year <= report_year) %>%
  mutate(BY = Brood.Year) %>%
  mutate(Brood.Year = factor(Brood.Year))%>%
  mutate(color = case_when(Sac.Val.Year.Type == "C" ~ "#D55E00",
                           Sac.Val.Year.Type == "D" ~ "#E69F00",
                           Sac.Val.Year.Type == "AN" ~ "#009E73",
                           Sac.Val.Year.Type == "BN" ~  "black",
                           Sac.Val.Year.Type == "W" ~ "#0072B2")) %>%
  mutate(Brood.Year.Type = paste0(Brood.Year, " (", Sac.Val.Year.Type, ")" ))

tdm_long <- tdm %>%
  select(Brood.Year.Type, color,
         `Temperature Attributed Mortality` = TDM_NOAA_percent, 
         `Egg-to-Fry Survival` = ETF_survival, 
         `Unattributed Mortality` = unexplained_mortality) %>%
  pivot_longer(cols = `Temperature Attributed Mortality`:`Unattributed Mortality`, names_to = "Fate", values_to = "Percent") %>%
  mutate(Percent_label = round(Percent)) 
```

```{r }
avg.ETF = mean(jpi$ETF_Survival)
current.ETF = jpi$ETF_Survival[1]

dir_etf <- ifelse(current.ETF<avg.ETF, "below", "above")
```


**Egg-to-Fry Metrics**

-   **Total potential eggs:** `r paste(scales::comma(eggs$value[eggs$brood_year == report_year]), "eggs")`
    -   **10-year average:** `r paste(scales::comma(mean(tenyear$value, na.rm=TRUE)), "eggs")`
    -   **20-year average:** `r paste(scales::comma(mean(twentyyear$value, na.rm=TRUE)), "eggs")`
-   **Fry-equivalents at RBDD (JPE Letter):** `r scales::comma(as.numeric(jpi$value[jpi$brood_year == report_year]))`. 
    -   **10-year average:** `r scales::comma(mean(as.numeric(jpi_tenyear$value), na.rm = TRUE))` including 2011, 2014-2017, 2021
-   **Egg to Fry Survival (ETF Survival):** ETF Survival in `r report_year` was `r dir_etf` the average ETF between 2002 and `r report_year` at `r current.ETF`% (Figure \@ref(fig:ETFSurv-fig)). 
    -   The average ETF from `r min(year(jpi$BY))` to `r report_year` was `r avg.ETF`%


#### SacPAS Fish Model 

-   Redds exposed to Tcritical = 11.82°C (53.28°F) are shown in Figure X.
    -   Pre-hatching exposure: 
    -   Pre-emergence exposure: 
-   Estimated total egg-to-fry emergence survival:
    -   Temperature-dependent survival: 
-   TDM
    -   Spawner density-based survival:
    ‒   Background survival: 
    ‒	  Dewater-based survival: 
    ‒	  Survival by reach is shown in Table X


Table of Survival by Reach (Fish Model)
```{r survByReachTab}

```

```{r totaleggs-fig, fig.cap = "Potential Total Eggs in the Upper Sacramento"}
ggplot(eggs) + 
  geom_col(aes(x = brood_year, y = value), fill = "chartreuse4") +
  geom_segment(aes(x = report_year-10+0.5, xend = report_year+0.5, y = mean(tenyear$value, na.rm = TRUE), yend = mean(tenyear$value, na.rm = TRUE)), linetype = "dashed", size = 0.6) + 
  geom_segment(aes(x = report_year-20+0.5, xend = report_year+0.5, y = mean(twentyyear$value, na.rm = TRUE), yend = mean(twentyyear$value, na.rm = TRUE)), linetype = "dotted", size = 0.7) + 
  labs(y = "Total eggs", x = "Year") + 
  theme_bw()
```

```{r TDM-etf-fig, message = FALSE, warning = FALSE, echo = FALSE, fig.cap = paste0("Annual Percent of Egg to Fry Survival, Temperature-Dependent Mortality, and Unattributed Survival from 2002 to ",report_year, ". Labels in parentheses indicate Water Year Type.")}
yrcolors <- rev(tdm$color)

(plot_tdm <- ggplot(tdm_long, aes(Brood.Year.Type, Percent, fill = Fate)) + 
  geom_col(width = 0.65, alpha = 0.9) +
  geom_text(aes(label = Percent_label), position = position_stack(vjust = 0.5), size = 4.5) +
  scale_fill_manual(values = c("goldenrod","steelblue" ,"gray70")) + 
  labs(x = "Brood Year") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, size = 11.5, colour = yrcolors),
        axis.text.y = element_text(size = 12),
        legend.position = "bottom",
        legend.title = element_blank()))
```

```{r ETFSurv-fig, echo = FALSE}
tenyear_etf = jpi %>% filter(BY > report_year-10 & BY<= report_year)
twentyyear_etf = jpi %>% filter(BY > report_year-20 & BY<= report_year)

(plot_etf <- ggplot() + 
  geom_col(data = jpi, aes(BY, ETF_Survival), fill = "#007396", alpha = 0.8, width = 0.8) +
  geom_text(data = jpi, aes(BY, ETF_Survival +1, label = ETF_Survival_lab), size =  3) + 
  geom_segment(aes(x = report_year-10+0.5, xend = report_year+0.5, 
                   y = mean(tenyear_etf$ETF_Survival), 
                   yend = mean(tenyear_etf$ETF_Survival)), 
               linetype = "dashed", size = 0.6) + 
  geom_segment(aes(x = report_year-20+0.5, xend = report_year+0.5, 
                   y = mean(twentyyear_etf$ETF_Survival), 
                   yend = mean(twentyyear_etf$ETF_Survival)),
               linetype = "dotted", size = 0.6) + 
  labs(y = "Egg-to-Fry Survival (%)") +
    # scale_y_continuous(expand = c(0,0)) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank()))
```


SacPAS Fish Model Results for Temperature Exposure (Plot)
```{r tempExposure-fig}

```

### Emergence

**Placeholder for SacPAS fish model output for emergence timing**
```{r}

```


SacPAS fish model estimates for emergence:

- **First occupancy:**
- **Emergence:**
      - **First:**
      - **Mean:**
      - **Last:**

SacPAS Fish Model Results for Redd Occupation and Emergency Timing (Plot)
```{r}

```

### Redd Dewatering 

I don't know if these two are the same redd (redd ID has 2 numbers switched around)
What is the unit for water depth?
```{r}
dewater <- read_csv("data_raw/current_year_dewatering.csv")

dewater_clean <- dewater %>%
  filter(dewateredstatus!= "Not Dewatered") %>%
  group_by(reddid)%>%
  arrange(date) %>%
  slice(1) %>%
  ungroup() %>%
  select(date, rivermile, RiverSection, depth,  flowkwk) %>%
  rename(Date = date,
         `River Mile` = rivermile,
         `River Section` = RiverSection,
         `Water Depth` = depth,
         `Flow at Keswick Dam (cfs)` = flowkwk)

```

- `r nrow(dewater_clean)` redds were dewatered in report_year (Table \@ref(tab:dewateredRedds)).

```{r dewateredRedds}
kable(dewater_clean,
      label = NA,
      vline = "",
      caption = paste("Dewatered Redds in", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") 
```

