# Upper Sacramento Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Upper Sacramento River.

```{r setup3, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)
library(readr)
library(here)
library(rvest)

library(kableExtra)
library(flextable)
library(CDECRetrieve)
source("functions.R")
source("parameters.R")
```

## Habitat Attributes

---

## Environmental Drivers

---

### Flow

```{r KWKBNDflowjuv-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Flows (cfs) at Sacramento River at Keswick (KWK) and Sacramento River at Bend Bridge (BND) in July through September",report_year, "and over the 10-year average"), fig.width = 8, fig.height = 6}
flow_kwk_bnd_juv <- readRDS(paste0("data_raw/flow_kwk_bnd_plot_data_", year(start), "-", year(end), ".rds")) %>%
  filter(month %in% c("July", "August", "September", "October", "November", "December"))

ggplotly(ggplot(flow_kwk_bnd_juv) + 
  geom_line(aes(date, flow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots )
```

```{r KWKBNDflowjuv-tab}
flow_kwk_bnd_monthly_us <- readRDS(paste0("data_raw/flow_kwk_bnd_monthly_", 
                                           year(start), "-", year(end), ".rds")) %>%
  filter(month %in% c("July", "August", "September", "October", "November", "December"))


flow_kwk_bnd_monthly_us_t <- flow_kwk_bnd_monthly_us

colnames(flow_kwk_bnd_monthly_us_t) <- stringr::str_to_title(colnames(flow_kwk_bnd_monthly_us_t))

kable(flow_kwk_bnd_monthly_us_t,
      label = NA,
      vline = "",
      caption = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Sacramento River at Keswick (KWK) and Sacramento River at Bend Bridge (BND) in July through December", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(6,extra_css = "border-bottom: 1px solid;")


# flextable(flow_kwk_bnd_monthly_us)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = 6, part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)")
```

```{r echo = FALSE}
monthly_kwk_us <- flow_kwk_bnd_monthly_us %>% filter(station == "KWK")
max_flow_kwk_us <- max(monthly_kwk_us$max)
max_mean_flow_kwk_us <- max(monthly_kwk_us$mean)
max_flow_kwk_month_us <- monthly_kwk_us %>% filter(max == max_flow_kwk_us) %>% select(month)
max_mean_flow_kwk_month_us <- monthly_kwk_us %>% filter(mean == max_mean_flow_kwk_us) %>% select(month)

monthly_bnd_us <- flow_kwk_bnd_monthly_us %>% filter(station == "BND")
max_flow_bnd_us <- max(monthly_bnd_us$max)
max_mean_flow_bnd_us <- max(monthly_bnd_us$mean)
max_flow_bnd_month_us <- monthly_bnd_us %>% filter(max == max_flow_bnd_us) %>% select(month)
max_mean_flow_bnd_month_us <- monthly_bnd_us %>% filter(mean == max_mean_flow_bnd_us) %>% select(month)
```

-   **Keswick:** Peak flows were **`r max_flow_kwk_us`** cfs and occurred in **`r max_flow_kwk_month_us[1]`**. The highest mean flows were **`r max_mean_flow_kwk_us`** cfs and occurred in **`r max_mean_flow_kwk_month_us`**.
-   **Bend Bridge:** Peak flows were **`r max_flow_bnd_us`** cfs and occurred in **`r max_flow_bnd_month_us[1]`**. The highest mean flows were **`r max_mean_flow_bnd_us`** cfs and occurred in **`r max_mean_flow_bnd_month_us`**.

---

### Water Temperature

```{r wtempBND-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Water Temperature (degF) at Sacramento River at Bend (BND) in",report_year,"and 10-year average between July and December.") , fig.width = 8, fig.height = 4.5}

wtemp_bnd_plot_data <- readRDS(paste0("data_raw/wtemp_BND_plot_data_", year(start), "-", year(end), ".rds")) %>%
  filter(month >=7 & month<=12)

ggplotly(ggplot(wtemp_bnd_plot_data) + geom_line(aes(date, WaterTemp, color = plot_year, linetype = plot_year)) +
  geom_hline(yintercept  = 56, linetype = "dotdash", color = "gray50", size  = 0.7) + 
  facet_wrap(~station, nrow = 2) + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Water Temperature (°F)") +
  theme_plots )

```

```{r wtempBNDjuv-tab}
wtemp_bnd_monthly_us <- readRDS(paste0("data_raw/wtemp_BND_monthly_", 
                                           year(start), "-", year(end), ".rds")) %>% filter(month %in% c("July", "August", "September", "October", "November", "December"))

wtemp_bnd_monthly_us_t <- wtemp_bnd_monthly_us

colnames(wtemp_bnd_monthly_us_t) <- stringr::str_to_title(colnames(wtemp_bnd_monthly_us_t))

kable(wtemp_bnd_monthly_us_t,
      label = NA,
      vline = "",
      caption = paste("Mean, Maximum, Minimum Monthly Water Temperature (degF) at Sacramento River at Bend Bridge (BND) in July through December", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria")


# flextable(wtemp_bnd_monthly_us)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (degF)", max = "Max (degF)", min =  "Min (degF)")
```

```{r echo = FALSE}
monthly_wtemp_bnd_us <- wtemp_bnd_monthly_us %>% filter(station == "BND")
max_wtemp_bnd_us <- max(monthly_wtemp_bnd_us$max)
max_mean_wtemp_bnd_us <- max(monthly_wtemp_bnd_us$mean)
max_wtemp_bnd_us_month <- monthly_wtemp_bnd_us %>% filter(max == max_wtemp_bnd_us) %>% select(month)
max_mean_wtemp_bnd_us_month <- monthly_wtemp_bnd_us %>% filter(mean == max_mean_wtemp_bnd_us) %>% select(month)
```

**Summary**

- In `r report_year` water temperature was below average for most of the season between July and December. 
- **Sacramento River at Bend Bridge:** Maximum water temperature was **`r max_wtemp_bnd_us`** degrees F and occurred in **`r max_wtemp_bnd_us_month`**. The highest mean water temperature was **`r max_mean_wtemp_bnd_us`** degrees F and occurred in **`r max_mean_wtemp_bnd_us_month`**.

---

### Dissolved Oxygen

```{r doBNDjuv-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Dissolved Oxygen (mg/L) at Sacramento River at Bend Bridge (BND) in July through December",report_year,"and 10-year average."), fig.width = 8, fig.height = 4.5}

do_bnd_plot_data <- readRDS(paste0("data_raw/do_BND_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month >=7 & month<=12)

ggplotly(ggplot(do_bnd_plot_data) + geom_line(aes(date, DO, color = plot_year, linetype = plot_year)) +
  geom_hline(yintercept  = 6, linetype = "dotdash", color = "gray50", size  = 0.7) + 
  facet_wrap(~station, nrow = 2) + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Dissolved Oxygen (mg/L)") +
  theme_plots )
```

```{r doBNDjuv-tab}
do_bnd_monthly_us <- readRDS(paste0("data_raw/do_bnd_monthly_", 
                                           year(start), "-", year(end2), ".rds"))

do_bnd_df <- readRDS(paste0("data_raw/do_cdec_BND_", year(start), "-", year(end2), ".rdsxz")) %>%
  filter(month >6 & month<=12)

do_bnd_monthly_us <- f_monthly_extrayear_thresh(do_bnd_df, DO, 6) %>%
  arrange(station) %>%
  select(-month_num)

do_bnd_monthly_us_t <- do_bnd_monthly_us %>%
  rename(`Days < 6mg/L` = flag_days)

colnames(do_bnd_monthly_us_t) <- stringr::str_to_title(colnames(do_bnd_monthly_us_t))

kable(do_bnd_monthly_us_t,
      label = NA,
      vline = "",
      caption = paste("Mean, Maximum, Minimum Monthly Dissolved Oxygen (mg/L) at Sacramento River at Bend Bridge (BND) in July through December", report_year, ". Days less than 6 mg/L indicates the number of days per month that experienced at least 1 hour where DO was less than 6 mg/L."),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") 

# flextable(do_bnd_monthly_us)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (mg/L)", min =  "Min (mg/L)", flag_days = "Days < 6 mg/L")
```

```{r echo = FALSE}
monthly_bnd_us <- do_bnd_monthly_us %>% filter(station == "BND")
min_do_bnd_us <- min(monthly_bnd_us$min)
min_mean_do_bnd_us <- min(monthly_bnd_us$mean)
min_do_bnd_us_month <- monthly_bnd_us %>% filter(min == min_do_bnd_us) %>% select(month)
min_mean_do_bnd_us_month <- monthly_bnd_us %>% filter(mean == min_mean_do_bnd_us) %>% select(month)
```

**Summary**

-   **Sacramento River at Bend Bridge:** Minimum dissolved oxygen was **`r min_do_bnd_us`** mg/L and occurred in **`r min_do_bnd_us_month[1]`**. The lowest mean dissolved oxygen was **`r min_mean_do_bnd_us`** mg/L and occurred in **`r min_mean_do_bnd_us_month`**.

---

### Turbidity
```{r TurbBNDRDB-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Turbidity at Sacramento River at Bend Bridge (BND) and Red Bluff Diversion Dam (RDB) in",report_year, "and 10-year average between July and December. Turbidity data have not undergone QC, other than values filtered to less than 300 NTU."), fig.width = 8, fig.height = 5}

turb_bnd_rdb_plot_data <- readRDS(paste0("data_raw/turb_BND_RDB_plot_data_", year(start), "-", year(end), ".rds")) %>%
  filter(Turbidity < 300)%>%
  filter(month >=7 & month<=12)

ggplotly(ggplot(turb_bnd_rdb_plot_data) + 
  geom_line(aes(date, Turbidity, color = plot_year, linetype = plot_year)) +
  # geom_point(aes(date, Turbidity, color = plot_year))+
  facet_wrap(~station, nrow = 2, scales = "free_y") + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Turbidity (NTU)") +
  theme_plots )
```

```{r turbBNDjuv-tab}
turb_bnd_rdb_monthly_us <- readRDS(paste0("data_raw/turb_BND_RDB_monthly_", 
                                           year(start), "-", year(end), ".rds")) %>%
  filter(month %in% c("July", "August", "September", "October", "November", "December"))

turb_bnd_rdb_monthly_us_t <- turb_bnd_rdb_monthly_us

colnames(turb_bnd_rdb_monthly_us_t) <- stringr::str_to_title(colnames(turb_bnd_rdb_monthly_us_t))

kable(turb_bnd_rdb_monthly_us_t,
      label = NA,
      vline = "",
      caption = paste("Mean, Maximum, Minimum Monthly Turbidity (NTU) at Sacramento River at Bend Bridge (BND) and Red Bluff Diversion Dam (RDB) in July through December", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(6,extra_css = "border-bottom: 1px solid;")



# flextable(turb_bnd_rdb_monthly_us)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = c(6,12), part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)")
```

```{r echo = FALSE}
monthly_bnd_turb_us <- turb_bnd_rdb_monthly_us %>% filter(station == "BND")
min_turb_bnd_us <- min(monthly_bnd_turb_us$min)
min_mean_turb_bnd_us <- min(monthly_bnd_turb_us$mean)
min_turb_bnd_us_month <- monthly_bnd_turb_us %>% filter(min == min_turb_bnd_us) %>% select(month)
min_mean_turb_bnd_us_month <- monthly_bnd_turb_us %>% filter(mean == min_mean_turb_bnd_us) %>% select(month)

monthly_rdb_turb_us <- turb_bnd_rdb_monthly_us %>% filter(station == "RDB")
min_turb_rdb_us <- min(monthly_rdb_turb_us$min)
min_mean_turb_rdb_us <- min(monthly_rdb_turb_us$mean)
min_turb_rdb_us_month <- monthly_rdb_turb_us %>% filter(min == min_turb_rdb_us) %>% select(month)
min_mean_turb_rdb_us_month <- monthly_rdb_turb_us %>% filter(mean == min_mean_turb_rdb_us) %>% select(month)
```

**Summary**

-   **Sacramento River at Bend Bridge:** Minimum turbidity was **`r min_turb_bnd_us`** FNU and occurred in **`r min_turb_bnd_us_month[1,]`** and **`r min_turb_bnd_us_month[2,]`**. The lowest mean turbidity was **`r min_mean_turb_bnd_us`** FNU and occurred in **`r min_mean_turb_bnd_us_month`**. Turbidity was below average in parts of August and September and similar at other times of the season. 
-   **Red Bluff Diversion Dam:** Minimum turbidity was **`r min_turb_rdb_us`** FNU and occurred in **`r min_turb_rdb_us_month`**. The lowest mean turbidity was **`r min_mean_turb_rdb_us`** FNU and occurred in **`r min_mean_turb_rdb_us_month`**. Turbidity was below average between September and mid-December and similar at other times of the season 


---

## Biological Response

---

### Fry abundance 

#### Estimated Fry Passage at RBDD - Placeholder - use Report or raw data?
* Percent Fry Passage at RBDD (fry/fry+smolts)
```{r}

```


#### Fry-equivalent JPI

```{r JPI-fig, message = FALSE, warning = FALSE, echo = FALSE,fig.cap = paste("Annual JPI from 2002 to",report_year)}

library(scales)
jpi <- read.csv("data_raw/JPI_2002_2023.csv") %>%
  filter(BY <= report_year) %>%
  rename(JPI = Fry.Equivalent.JPI,
         ETF_Survival = ETF.Survival.Rate....) %>%
  select(BY, JPI, ETF_Survival) %>%
  mutate(JPI = JPI/1000000,
         JPI_lab = round(JPI, 2),
         ETF_Survival_lab = round(ETF_Survival)) %>%
  mutate(BY = factor(BY))

avg.JPI = mean(jpi$JPI)
current.JPI = jpi$JPI[1]

(plot_jpi <- ggplot(jpi) + 
  geom_col(aes(BY, JPI), fill = "#C69214", alpha = 0.8, width = 0.8) +
  geom_text(aes(BY, JPI+0.15, label = JPI_lab), size = 3) + 
  geom_hline(yintercept = avg.JPI, linetype = "dashed") + 
  labs(y = "Juvenile Production Index (millions)") +
  scale_y_continuous() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank()))
```

* By year
* RBDD RST Data 

```{r echo = FALSE}
dir_jpi <- ifelse(current.JPI<avg.JPI, "below", "above")
```

-   **Juvenile Production Index** JPI in `r report_year` was `r dir_jpi` the average JPI between 2002 and `r report_year` at `r current.JPI`.


2. Condition/ Growth
* Fork length by year

3. Migration Timing
* RBDD RST Data

4. Fry-to-Smolt Survival
* Model?

---

### Migration Timing 

```{r}
rbdd_timing <- read_csv("data_raw/migration_timing_rbdd.csv")
rbdd_by <- rbdd_timing %>% 
  filter(brood_year == report_year) %>%
  mutate_at(vars(first_passage_date:last_passage_date), as_date, format = "%m/%d/%Y")
rbdd_median <- rbdd_timing %>%
  filter(stringr::str_detect(brood_year, "Median"))%>%
  mutate_at(vars(first_passage_date:last_passage_date), as_date, format = "%m/%d")
```

Passage at RBDD: 

- **First:** 
    - BY`r report_year`: `r format(rbdd_by$first_passage_date, "%B %d, %Y")`
    - 10-year median: `r format(rbdd_median$first_passage_date, "%B %d")`
- **Middle 50% (25% to 75%):**
    - BY`r report_year`: `r format(rbdd_by$x25_percent_passage_date, "%B %d, %Y")` to `r format(rbdd_by$x75_percent_passage_date, "%B %d, %Y")`
    - 10-year median: `r format(rbdd_median$x25_percent_passage_date, "%B %d")` to `r format(rbdd_median$x75_percent_passage_date, "%B %d")`
- **Last:**
    - BY`r report_year`: `r format(rbdd_by$last_passage_date, "%B %d, %Y")`
    - 10-year median: `r format(rbdd_median$last_passage_date, "%B %d")` 


```{r rbdd-timing-fig, fig.cap = "RBDD Timing"}
# rbdd_link <- paste0("https://www.cbr.washington.edu/sacramento/data/php/rpt/hrt.php?species=CHN%3AWinter&loc=RBDD&years=10&typeData=raw&histYear=", report_year, "&outputFormat=hrtplotOnly")
# knitr::include_graphics(rbdd_link)
```

---

### Stranding

```{r}
stranding <- read_csv("data_raw/stranding_data.csv") %>%
  mutate(Date = date(ymd_hms(DateTime)),
         Year = year(Date)) 

flow_stranding <- flow_kwk_bnd_juv %>% 
  filter(year_type == "mean") %>% 
  pivot_wider(names_from = station, values_from = flow) %>%
  select(date, KWK, BND)

section_url <- "https://www.cbr.washington.edu/sacramento/data/query_stranding.html"
section <- section_url %>%
  read_html() %>%
  html_nodes(xpath='//*[@id="query"]/table') %>%
  html_table()
section_names <- (section[[1]]) %>%
  rename(Section = Survey)

stranding_current <- stranding%>%
  filter((Year==report_year & month(Date)>4) | (Year == report_year+1 & month(Date)<5), 
`Winter Run Natural`!=0) %>%
  select(Date, RiverSection, Section=riversectioncode, `Winter Run Natural`, `Winter Run Natural Mortality`) %>%
  group_by(Date, RiverSection, Section) %>% 
  summarize(Count = sum(`Winter Run Natural`)) %>%
  ungroup() %>%
  rename(`River Section` = RiverSection) %>%
  left_join(flow_stranding %>% select(Date = date, KWK,BND)) %>%
  mutate(`Flow (cfs)` = case_when(Section != 8 ~ round(KWK),
                          Section == 8 ~ round(BND))) %>%
  mutate(`Flow Gage` = case_when(Section != 8 ~ "KWK",
                          Section == 8 ~ "BND")) %>%
  select(-KWK, -BND) %>%
  left_join(section_names %>% select(Section, `River Miles`), by = "Section") %>%
  select(Date, `Section Number` = Section, `Section Name` = `River Section`, `River Miles`, everything()) %>%
  arrange(`Section Number`)

total_stranded <- sum(stranding_current$Count)
```

A total of `r total_stranded` juveniles were stranded. 

```{r juvstrandingUS}
kable(stranding_current,
      label = NA,
      vline = "",
      caption = paste("Juvenile Stranding in", report_year),
      valign = "t") %>%
  kable_classic(html_font = "Cambria")
```

---

### Condition

#### RBDD Size
```{r rbdd-fl-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Fork Length Distribution over Time, RBDD RST" }
fl_rbdd <- read.csv("data_raw/rbdd_juv_fl.csv") %>%
  mutate(date = ymd(date_yyyy_mm_dd))

ggplot(fl_rbdd) + 
  geom_errorbar(aes(date, ymin = length_min, ymax = length_max)) +
  geom_point(aes(date, length), color = "steelblue3")+
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") + 
  labs(y = "Fork Length (mm)")+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_blank())
```

```{r rbdd-flhist-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Fork Length Distribution over Time, RBDD RST" }
fl_rbdd <- read.csv("data_raw/raw_wr_rbdd.csv") %>%
  mutate(date = ymd(start_date)) %>%
  filter(year(date) >=report_year & year(date) < report_year +2)

ggplot(fl_rbdd) + 
  geom_histogram(aes(fork_length), color = "black") +
  theme_bw()
```


