# Upper Sacramento Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Upper Sacramento River.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)

library(kableExtra)
library(flextable)
library(CDECRetrieve)
source("functions.R")
source("parameters.R")
```

## Habitat Attributes

## Environmental Drivers

### Flow

```{r KWKBNDflowjuv-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Flows (cfs) at Sacramento River at Keswick (KWK) and Sacramento River at Bend Bridge (BND) in July through September",report_year, "and over the 10-year average"), fig.width = 8, fig.height = 6}
flow_kwk_bnd_juv <- readRDS(paste0("data_raw/flow_kwk_bnd_plot_data_", year(start), "-", year(end), ".rds")) %>%
  filter(month %in% c("July", "August", "September", "October", "November", "December"))

ggplotly(ggplot(flow_kwk_bnd_juv) + 
  geom_line(aes(date, flow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots )
```

```{r KWKBNDflowjuv-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Sacramento River at Keswick (KWK) and Sacramento River at Bend Bridge (BND) in July through Decemeber", report_year)}
flow_kwk_bnd_monthly_us <- readRDS(paste0("data_raw/flow_kwk_bnd_monthly_", 
                                           year(start), "-", year(end), ".rds")) %>%
  filter(month %in% c("July", "August", "September", "October", "November", "December"))

flextable(flow_kwk_bnd_monthly_us)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = 6, part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)")
```

```{r echo = FALSE}
monthly_kwk_us <- flow_kwk_bnd_monthly_us %>% filter(station == "KWK")
max_flow_kwk_us <- max(monthly_kwk_us$max)
max_mean_flow_kwk_us <- max(monthly_kwk_us$mean)
max_flow_kwk_month_us <- monthly_kwk_us %>% filter(max == max_flow_kwk_us) %>% select(month)
max_mean_flow_kwk_month_us <- monthly_kwk_us %>% filter(mean == max_mean_flow_kwk_us) %>% select(month)

monthly_bnd_us <- flow_kwk_bnd_monthly_us %>% filter(station == "BND")
max_flow_bnd_us <- max(monthly_bnd_us$max)
max_mean_flow_bnd_us <- max(monthly_bnd_us$mean)
max_flow_bnd_month_us <- monthly_bnd_us %>% filter(max == max_flow_bnd_us) %>% select(month)
max_mean_flow_bnd_month_us <- monthly_bnd_us %>% filter(mean == max_mean_flow_bnd_us) %>% select(month)
```

-   **Keswick:** Peak flows were **`r max_flow_kwk_us`** cfs and occurred in **`r max_flow_kwk_month_us[1]`**. The highest mean flows were **`r max_mean_flow_kwk_us`** cfs and occurred in **`r max_mean_flow_kwk_month_us`**.
-   **Bend Bridge:** Peak flows were **`r max_flow_bnd_us`** cfs and occurred in **`r max_flow_bnd_month_us[1]`**. The highest mean flows were **`r max_mean_flow_bnd_us`** cfs and occurred in **`r max_mean_flow_bnd_month_us`**.

### Stranding

### Water Temperature

```{r wtempBND-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Water Temperature (degF) at Sacramento River at Bend (BND) in",report_year,"and 10-year average between July and December.") , fig.width = 8, fig.height = 4.5}

wtemp_bnd_plot_data <- readRDS(paste0("data_raw/wtemp_BND_plot_data_", year(start), "-", year(end), ".rds")) %>%
  filter(month >=7 & month<=12)

ggplotly(ggplot(wtemp_bnd_plot_data) + geom_line(aes(date, WaterTemp, color = plot_year, linetype = plot_year)) +
  geom_hline(yintercept  = 56, linetype = "dotdash", color = "gray50", size  = 0.7) + 
  facet_wrap(~station, nrow = 2) + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Water Temperature (°F)") +
  theme_plots )

```
```{r wtempBNDjuv-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Water Temperature (degF) at Sacramento River at Bend Bridge (BND) in July through December", report_year)}
wtemp_bnd_monthly_us <- readRDS(paste0("data_raw/wtemp_BND_monthly_", 
                                           year(start), "-", year(end), ".rds")) %>% filter(month %in% c("July", "August", "September", "October", "November", "December"))

flextable(wtemp_bnd_monthly_us)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (degF)", max = "Max (degF)", min =  "Min (degF)")
```

```{r echo = FALSE}
monthly_wtemp_bnd_us <- wtemp_bnd_monthly_us %>% filter(station == "BND")
max_wtemp_bnd_us <- max(monthly_wtemp_bnd_us$max)
max_mean_wtemp_bnd_us <- max(monthly_wtemp_bnd_us$mean)
max_wtemp_bnd_us_month <- monthly_wtemp_bnd_us %>% filter(max == max_wtemp_bnd_us) %>% select(month)
max_mean_wtemp_bnd_us_month <- monthly_wtemp_bnd_us %>% filter(mean == max_mean_wtemp_bnd_us) %>% select(month)
```

**Summary**

- In `r report_year` water temperature was below average for most of the season between July and December. 
- **Sacramento River at Bend Bridge:** Maximum water temperature was **`r max_wtemp_bnd_us`** degrees F and occurred in **`r max_wtemp_bnd_us_month`**. The highest mean water temperature was **`r max_mean_wtemp_bnd_us`** degrees F and occurred in **`r max_mean_wtemp_bnd_us_month`**.


### Dissolved Oxygen

```{r doBNDjuv-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Dissolved Oxygen (mg/L) at Sacramento River at Bend Bridge (BND) in July through December",report_year,"and 10-year average."), fig.width = 8, fig.height = 4.5}

do_bnd_plot_data <- readRDS(paste0("data_raw/do_BND_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month >=7 & month<=12)

ggplotly(ggplot(do_bnd_plot_data) + geom_line(aes(date, DO, color = plot_year, linetype = plot_year)) +
  geom_hline(yintercept  = 6, linetype = "dotdash", color = "gray50", size  = 0.7) + 
  facet_wrap(~station, nrow = 2) + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Dissolved Oxygen (mg/L)") +
  theme_plots )
```

```{r doBNDjuv-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Dissolved Oxygen (mg/L) at Sacramento River at Bend Bridge (BND) in July through December", report_year, ". Days less than 6 mg/L indicates the number of days per month that experienced at least 1 hour where DO was less than 6 mg/L.")}
do_bnd_monthly_us <- readRDS(paste0("data_raw/do_bnd_monthly_", 
                                           year(start), "-", year(end2), ".rds"))

do_bnd_df <- readRDS(paste0("data_raw/do_cdec_BND_", year(start), "-", year(end2), ".rdsxz")) %>%
  filter(month >6 & month<=12)
do_bnd_monthly_us <- f_monthly_extrayear_thresh(do_bnd_df, DO, 6) %>%
  arrange(station) %>%
  select(-month_num)

flextable(do_bnd_monthly_us)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (mg/L)", min =  "Min (mg/L)", flag_days = "Days < 6 mg/L")
```

```{r echo = FALSE}
monthly_bnd_us <- do_bnd_monthly_us %>% filter(station == "BND")
min_do_bnd_us <- min(monthly_bnd_us$min)
min_mean_do_bnd_us <- min(monthly_bnd_us$mean)
min_do_bnd_us_month <- monthly_bnd_us %>% filter(min == min_do_bnd_us) %>% select(month)
min_mean_do_bnd_us_month <- monthly_bnd_us %>% filter(mean == min_mean_do_bnd_us) %>% select(month)
```

**Summary**

-   **Sacramento River at Bend Bridge:** Minimum dissolved oxygen was **`r min_do_bnd_us`** mg/L and occurred in **`r min_do_bnd_us_month[1]`**. The lowest mean dissolved oxygen was **`r min_mean_do_bnd_us`** mg/L and occurred in **`r min_mean_do_bnd_us_month`**.


### Turbidity
```{r TurbBNDRDB-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Turbidity at Sacramento River at Bend Bridge (BND) and Red Bluff Diversion Dam (RDB) in",report_year, "and 10-year average between July and December. Turbidity data have not undergone QC, other than values filtered to less than 300 NTU."), fig.width = 8, fig.height = 5}

turb_bnd_rdb_plot_data <- readRDS(paste0("data_raw/turb_BND_RDB_plot_data_", year(start), "-", year(end), ".rds")) %>%
  filter(Turbidity < 300)%>%
  filter(month >=7 & month<=12)

ggplotly(ggplot(turb_bnd_rdb_plot_data) + 
  geom_line(aes(date, Turbidity, color = plot_year, linetype = plot_year)) +
  # geom_point(aes(date, Turbidity, color = plot_year))+
  facet_wrap(~station, nrow = 2, scales = "free_y") + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Turbidity (NTU)") +
  theme_plots )
```

```{r turbBNDjuv-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Turbidity (NTU) at Sacramento River at Bend Bridge (BND) and Red Bluff Diversion Dam (RDB) in July through December", report_year)}
turb_bnd_rdb_monthly_us <- readRDS(paste0("data_raw/turb_BND_RDB_monthly_", 
                                           year(start), "-", year(end), ".rds")) %>%
  filter(month %in% c("July", "August", "September", "October", "November", "December"))

flextable(turb_bnd_rdb_monthly_us)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(6,12), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)")
```

```{r echo = FALSE}
monthly_bnd_turb_us <- turb_bnd_rdb_monthly_us %>% filter(station == "BND")
min_turb_bnd_us <- min(monthly_bnd_turb_us$min)
min_mean_turb_bnd_us <- min(monthly_bnd_turb_us$mean)
min_turb_bnd_us_month <- monthly_bnd_turb_us %>% filter(min == min_turb_bnd_us) %>% select(month)
min_mean_turb_bnd_us_month <- monthly_bnd_turb_us %>% filter(mean == min_mean_turb_bnd_us) %>% select(month)

monthly_rdb_turb_us <- turb_bnd_rdb_monthly_us %>% filter(station == "RDB")
min_turb_rdb_us <- min(monthly_rdb_turb_us$min)
min_mean_turb_rdb_us <- min(monthly_rdb_turb_us$mean)
min_turb_rdb_us_month <- monthly_rdb_turb_us %>% filter(min == min_turb_rdb_us) %>% select(month)
min_mean_turb_rdb_us_month <- monthly_rdb_turb_us %>% filter(mean == min_mean_turb_rdb_us) %>% select(month)
```

**Summary**

-   **Sacramento River at Bend Bridge:** Minimum turbidity was **`r min_turb_bnd_us`** FNU and occurred in **`r min_turb_bnd_us_month[1,]`** and **`r min_turb_bnd_us_month[2,]`**. The lowest mean turbidity was **`r min_mean_turb_bnd_us`** FNU and occurred in **`r min_mean_turb_bnd_us_month`**. Turbidity was below average in parts of August and September and similar at other times of the season. 
-   **Red Bluff Diversion Dam:** Minimum turbidity was **`r min_turb_rdb_us`** FNU and occurred in **`r min_turb_rdb_us_month`**. The lowest mean turbidity was **`r min_mean_turb_rdb_us`** FNU and occurred in **`r min_mean_turb_rdb_us_month`**. Turbidity was below average between September and mid-December and similar at other times of the season 







## Biological Response

1. Fry abundance (Fry-equivalent JPI)

* By year
* RBDD RST Data 

2. Condition/ Growth
* Fork length by year

3. Migration Timing
* RBDD RST Data

4. Fry-to-Smolt Survival
* Model?

