# Upper Sacramento Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Upper Sacramento River.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
source("functions.R")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
theme_plots <- theme_bw() + theme(axis.text = element_text(size = 12),
                                  strip.text = element_text(size = 12),
                                  legend.text = element_text(size = 12),
                                  axis.title = element_text(size = 13),
                                  axis.title.x = element_blank(),
                                  legend.title = element_blank(),
                                  legend.position = "top",
                                  axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

## Habitat Attributes

1. Hatchery Influence (Juvenile Releases)

2. Juvenile Stranding

3. Pathogens/Disease

4. Contaminants

5. Habitat Capacity (Floodplain Connectivity)

6. Habitat Capacity: Depth/Shallow Water

7. In-Stream Habitat Capacity

## Environmental Drivers

1. Shasta Storage/Hydrology

2. Flows: Migration Cues

3. Flows at Keswick 

4. Turbidity and DO

5. Water Temperature


## Biological Response

1. Fry abundance (Fry-equivalent JPI)

* By year
* RBDD RST Data 

2. Condition/ Growth
* Fork length by year

3. Migration Timing
* RBDD RST Data

4. Fry-to-Smolt Survival
* Model?

