# Middle and Lower Sacramento Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Lower and Middle Sacramento River.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)

library(kableExtra)
library(flextable)
library(CDECRetrieve)
source("functions.R")
source("parameters.R")
```

## Habitat Attributes

1.  Habitat Capacity (Floodplain Connectivity)

2.  Habitat Capacity: Depth/Shallow Water

3.  In-Stream Habitat Capacity

### Storage and Flows

1.  Shasta Storage/Hydrology

2.  Flows: Migration Cues

#### Flow Conditions on the Middle and Lower Sacramento River

```{r HMCWLKVONflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Flows (cfs) at Sacramento River at Hamilton City (HMC), Sacramento River at Wilkins Slough (WLK) and Sacramento River at Verona (VON) from September",report_year, "through March", report_year+1, "and over the 10-year average"), fig.width = 8, fig.height = 7}
flow_hmc_wlk_von <- readRDS(paste0("data_raw/flow_hmc_wlk_von_plot_data_", lubridate::year(start), "-", lubridate::year(end2), ".rds")) %>%
  mutate(station = factor(station, levels = c("HMC", "WLK", "VON"))) %>%
  filter(!month%in%c("April", "May", "June")) %>%
  arrange(station)

plot_flow_hmc_wlk_von <- ggplot(flow_hmc_wlk_von) + 
  geom_line(aes(date, flow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 3) + 
  labs(y = "Flow (cfs)") +
  theme_plots 

plotly::ggplotly(plot_flow_hmc_wlk_von)
```

```{r HMCWLKVONflow-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum and Minimum Monthly Flows (cfs) at Sacramento River at Hamilton City (HMC), Sacramento River at Wilkins Slough (WLK) and Sacramento River at Verona (VON) from September", report_year, " through March", report_year+1)}
flow_hmc_wlk_von_df <- readRDS(paste0("data_raw/flow_hmc_wlk_von_df_", year(start), "-", year(end2), ".rdsxz"))

flow_hmc_wlk_von_monthly_ml <- f_monthly_extrayear(flow_hmc_wlk_von_df, flow) %>%
  filter(!month%in%c("April", "May", "June")) %>%
  mutate(station = factor(station, levels = c("HMC", "WLK", "VON"))) %>%
  select(-month_num) %>%
  arrange(station)

flextable(flow_hmc_wlk_von_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7,14), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)") 
```

```{r ,echo = FALSE}
monthly_hmc <- flow_hmc_wlk_von_monthly_ml %>% filter(station == "HMC")
max_flow_hmc <- max(monthly_hmc$max)
max_mean_flow_hmc <- max(monthly_hmc$mean)
max_flow_hmc_month <- monthly_hmc %>% filter(max == max_flow_hmc) %>% select(month)
max_mean_flow_hmc_month <- monthly_hmc %>% filter(mean == max_mean_flow_hmc) %>% select(month)

monthly_wlk <- flow_hmc_wlk_von_monthly_ml %>% filter(station == "WLK")
max_flow_wlk <- max(monthly_wlk$max)
max_mean_flow_wlk <- max(monthly_wlk$mean)
max_flow_wlk_month <- monthly_wlk %>% filter(max == max_flow_wlk) %>% select(month)
max_mean_flow_wlk_month <- monthly_wlk %>% filter(mean == max_mean_flow_wlk) %>% select(month)

monthly_von <- flow_hmc_wlk_von_monthly_ml %>% filter(station == "VON")
max_flow_von <- max(monthly_von$max)
max_mean_flow_von <- max(monthly_von$mean)
max_flow_von_month <- monthly_von %>% filter(max == max_flow_von) %>% select(month)
max_mean_flow_von_month <- monthly_von %>% filter(mean == max_mean_flow_von) %>% select(month)
```

**Summary**

-   **Hamilton City:** Peak flows were **`r max_flow_hmc`** cfs and occurred in **`r max_flow_hmc_month[1]`**. The highest mean flows were **`r max_mean_flow_hmc`** cfs and occurred in **`r max_mean_flow_hmc_month`**.

-   **Wilkins Slough:** Peak flows were **`r max_flow_wlk`** cfs and occurred in **`r max_flow_wlk_month[1]`**. The highest mean flows were **`r max_mean_flow_wlk`** cfs and occurred in **`r max_mean_flow_wlk_month`**.

-   **Verona:** Peak flows were **`r max_flow_von`** cfs and occurred in **`r max_flow_von_month[1]`**. The highest mean flows were **`r max_mean_flow_von`** cfs and occurred in **`r max_mean_flow_von_month`**.

### Environmental Drivers

#### Turbidity

```{r RDBFPTDO-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Turbidity at Red Bluff Diversion Dam (RDB) and Sacramento River at Freeport (FPT) from September", report_year, "through March", report_year+1)}

turb_rdb_fpt_plot_data <- readRDS(paste0("data_raw/turb_RDB_FPT_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(9,10,11,12,1,2,3))

ggplot(turb_rdb_fpt_plot_data) + geom_line(aes(date, Turbidity, color = plot_year, linetype = plot_year)) +
  geom_hline(yintercept  = 9, linetype = "dotdash", color = "gray50", size  = 0.7) + 
  facet_wrap(~station, nrow = 2, scales = "free_y") + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "2 weeks", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Turbidity (FNU)") +
  theme_plots 
```

```{r RDBFPTTurb-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Red Bluff Diversion Dam (RDB) and Sacramento River at Freeport (FPT) from September", report_year, "through March", report_year+1)}
turb_rdb_fpt_df <- readRDS(paste0("data_raw/turb_cdec_RDB_FPT_", year(start), "-", year(end2), ".rdsxz")) 

turb_rdb_fpt_monthly_ml <- f_monthly_extrayear(turb_rdb_fpt_df, Turbidity) %>%
  filter(!month%in%c("April", "May", "June")) %>%
  mutate(station = factor(station, levels = c("RDB", "FPT"))) %>%
  select(-month_num) %>%
  arrange(station)

flextable(turb_rdb_fpt_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = 7, part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (FNU)", max = "Max (FNU)", min =  "Min (FNU)") 
```

#### Water Temperature

```{r WLKwtemp-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Water Temperature (°F) at Sacramento River Below Wilkins Slough (WLK) in September", report_year, "through March", report_year+1, ". Days > 63°F indicates the number of days per month that experienced at least 1 hour where Water Temperature was greater than 63°F.")}

wtemp_wlk_df <- readRDS(paste0("data_raw/wtemp_cdec_WLK_", year(start), "-", year(end2), ".rdsxz")) 
wtemp_wlk_monthly_ml <- f_monthly_extrayear_thresh_greater(wtemp_wlk_df, WaterTemp, 63) %>%
  filter(month_num %in% c(9,10,11,12,1,2,3)) %>%
  select(-month_num)

flextable(wtemp_wlk_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  # hline(i = c(7), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (°F)", max = "Max (°F)", min =  "Min (°F)", flag_days = "Days > 63°F") 
```


#### Dissolved Oxygen

```{r RBDSRHDO-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Red Bluff Diversion Dam (RBD) and Sacramento River at Hood (SRH) in", report_year, "-", report_year+1, ". Days less than 6 mg/L indicates the number of days per month that experienced at least 1 hour where DO was less than 6 mg/L.")}
do_rdb_srh_df <- readRDS(paste0("data_raw/do_cdec_RDB_SRH_", year(start), "-", year(end2), ".rdsxz")) 

do_rdb_srh_monthly_ml <- f_monthly_extrayear_thresh(do_rdb_srh_df, DO, 6) %>%
  mutate(station = factor(station, levels = c("RDB", "SRH"))) %>%
  filter(month_num %in% c(9,10,11,12,1,2,3)) %>%
  arrange(station) %>%
  select(-month_num)

flextable(do_rdb_srh_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7,14), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)", flag_days = "Days < 6 mg/L") 
```

## Biological Response

Monitoring Sources for abundance, growth/size, migration timing/duration

-   Sac Trawl
-   Tisdale Weir
-   Knights Landing
-   GCID
-   DJFMP
-   Yolo Bypass
-   Chipps Island Trawl (Exit)
-   Genetic (Chipps, SWP/CVP, Knights Landing, Yolo Bypass)

1.  Abundance (Count) (IEP Monitoring)

-   Natural JPE
-   Hatchery JPE
-   SacPAS Fish Model (emerged fry)

2.  Condition

-   Growth/ Size

3.  Migration Timing

-   SacPAS style plots of historical and current year?

4.  Survival

-   Hatchery real-time: Calfish Track/ERDDAP
-   Natural Origin Smolt survival (O Farell et al. 2018)
-   Hatchery Origin Smolt survival
-   Modeled: \*\* Juvenile: STARS \*\* Fish Model
