# Middle and Lower Sacramento Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Lower and Middle Sacramento River.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
source("functions.R")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
theme_plots <- theme_bw() + theme(axis.text = element_text(size = 12),
                                  strip.text = element_text(size = 12),
                                  legend.text = element_text(size = 12),
                                  axis.title = element_text(size = 13),
                                  axis.title.x = element_blank(),
                                  legend.title = element_blank(),
                                  legend.position = "top",
                                  axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

## Habitat Attributes

1. Habitat Capacity (Floodplain Connectivity)

2. Habitat Capacity: Depth/Shallow Water

3. In-Stream Habitat Capacity

## Environmental Drivers

1. Shasta Storage/Hydrology

2. Flows: Migration Cues

3. Flows: In-River Flows

4. Turbidity 

5. Water Temperature

## Biological Response

Monitoring Sources for abundance, growth/size, migration timing/duration


* Sac Trawl
* Tisdale Weir
* Knights Landing
* GCID
* DJFMP
* Yolo Bypass
* Chipps Island Trawl (Exit)
* Genetic (Chipps, SWP/CVP, Knights Landing, Yolo Bypass)

1. Abundance (Count) (IEP Monitoring)

* Natural JPE
* Hatchery JPE
* SacPAS Fish Model (emerged fry)

2. Condition

* Growth/ Size

3. Migration Timing 

* SacPAS style plots of historical and current year?

4. Survival 

* Hatchery real-time: Calfish Track/ERDDAP
* Natural Origin Smolt survival (O Farell et al. 2018)
* Hatchery Origin Smolt survival
* Modeled:
  ** Juvenile: STARS
  ** Fish Model
