# Middle and Lower Sacramento Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Lower and Middle Sacramento River.


```{r setup4, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```


```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)
library(readr)

library(kableExtra)
library(flextable)
source("functions.R")
source("parameters.R")
```

## Habitat Attributes

1.  Habitat Capacity (Floodplain Connectivity)

2.  Habitat Capacity: Depth/Shallow Water

3.  In-Stream Habitat Capacity

### Storage and Flows

1.  Shasta Storage/Hydrology

2.  Flows: Migration Cues

#### Flow Conditions on the Middle and Lower Sacramento River

```{r HMCWLKVONflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Flows (cfs) at Sacramento River at Hamilton City (HMC), Sacramento River at Wilkins Slough (WLK) and Sacramento River at Verona (VON) from September",report_year, "through March", report_year+1, "and over the 10-year average"), fig.width = 8, fig.height = 7}
flow_hmc_wlk_von <- readRDS(paste0("data_raw/flow_hmc_wlk_von_plot_data_", lubridate::year(start), "-", lubridate::year(end2), ".rds")) %>%
  mutate(station = factor(station, levels = c("HMC", "WLK", "VON"))) %>%
  filter(!month%in%c("April", "May", "June")) %>%
  arrange(station)

ggplotly(ggplot(flow_hmc_wlk_von) + 
  geom_line(aes(date, flow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 3) + 
  labs(y = "Flow (cfs)") +
  theme_plots) 
```

```{r HMCWLKVONflow-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum and Minimum Monthly Flows (cfs) at Sacramento River at Hamilton City (HMC), Sacramento River at Wilkins Slough (WLK) and Sacramento River at Verona (VON) from September", report_year, " through March", report_year+1)}
flow_hmc_wlk_von_df <- readRDS(paste0("data_raw/flow_hmc_wlk_von_df_", year(start), "-", year(end2), ".rdsxz"))

flow_hmc_wlk_von_monthly_ml <- f_monthly_extrayear(flow_hmc_wlk_von_df, flow) %>%
  filter(!month%in%c("April", "May", "June")) %>%
  mutate(station = factor(station, levels = c("HMC", "WLK", "VON"))) %>%
  select(-month_num) %>%
  arrange(station)

flextable(flow_hmc_wlk_von_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7,14), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)") 
```

```{r ,echo = FALSE}
monthly_hmc <- flow_hmc_wlk_von_monthly_ml %>% filter(station == "HMC")
max_flow_hmc <- max(monthly_hmc$max)
max_mean_flow_hmc <- max(monthly_hmc$mean)
max_flow_hmc_month <- monthly_hmc %>% filter(max == max_flow_hmc) %>% select(month)
max_mean_flow_hmc_month <- monthly_hmc %>% filter(mean == max_mean_flow_hmc) %>% select(month)

monthly_wlk <- flow_hmc_wlk_von_monthly_ml %>% filter(station == "WLK")
max_flow_wlk <- max(monthly_wlk$max)
max_mean_flow_wlk <- max(monthly_wlk$mean)
max_flow_wlk_month <- monthly_wlk %>% filter(max == max_flow_wlk) %>% select(month)
max_mean_flow_wlk_month <- monthly_wlk %>% filter(mean == max_mean_flow_wlk) %>% select(month)

monthly_von <- flow_hmc_wlk_von_monthly_ml %>% filter(station == "VON")
max_flow_von <- max(monthly_von$max)
max_mean_flow_von <- max(monthly_von$mean)
max_flow_von_month <- monthly_von %>% filter(max == max_flow_von) %>% select(month)
max_mean_flow_von_month <- monthly_von %>% filter(mean == max_mean_flow_von) %>% select(month)
```

#### Juvenile WRCS Rescued During Stranding Surveys

Do we have this data?


**Summary**

-   **Hamilton City:** Peak flows were **`r max_flow_hmc`** cfs and occurred in **`r max_flow_hmc_month[1]`**. The highest mean flows were **`r max_mean_flow_hmc`** cfs and occurred in **`r max_mean_flow_hmc_month`**.

-   **Wilkins Slough:** Peak flows were **`r max_flow_wlk`** cfs and occurred in **`r max_flow_wlk_month[1]`**. The highest mean flows were **`r max_mean_flow_wlk`** cfs and occurred in **`r max_mean_flow_wlk_month`**.

-   **Verona:** Peak flows were **`r max_flow_von`** cfs and occurred in **`r max_flow_von_month[1]`**. The highest mean flows were **`r max_mean_flow_von`** cfs and occurred in **`r max_mean_flow_von_month`**.

### Environmental Drivers

#### Turbidity

```{r RDBFPTDO-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Daily Turbidity at Red Bluff Diversion Dam (RDB) and Sacramento River at Freeport (FPT) from September", report_year, "through March", report_year+1), fig.width = 8, fig.height = 7}

turb_rdb_fpt_plot_data <- readRDS(paste0("data_raw/turb_RDB_FPT_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(9,10,11,12,1,2,3))

ggplotly(ggplot(turb_rdb_fpt_plot_data) + geom_line(aes(date, Turbidity, color = plot_year, linetype = plot_year)) +
  geom_hline(yintercept  = 9, linetype = "dotdash", color = "gray50", size  = 0.7) + 
  facet_wrap(~station, nrow = 2, scales = "free_y") + 
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE) + 
  scale_x_date(date_breaks = "2 weeks", date_labels = "%b %d") +
  scale_linetype_manual(values = c("dashed", "solid", "solid"))+
  labs(y = "Turbidity (FNU)") +
  theme_plots )
```

```{r RDBFPTTurb-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Red Bluff Diversion Dam (RDB) and Sacramento River at Freeport (FPT) from September", report_year, "through March", report_year+1)}
turb_rdb_fpt_df <- readRDS(paste0("data_raw/turb_cdec_RDB_FPT_", year(start), "-", year(end2), ".rdsxz")) 

turb_rdb_fpt_monthly_ml <- f_monthly_extrayear(turb_rdb_fpt_df, Turbidity) %>%
  filter(!month%in%c("April", "May", "June")) %>%
  mutate(station = factor(station, levels = c("RDB", "FPT"))) %>%
  select(-month_num) %>%
  arrange(station)

flextable(turb_rdb_fpt_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = 7, part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (FNU)", max = "Max (FNU)", min =  "Min (FNU)") 
```


```{r echo = FALSE}
monthly_fpt_turb_ml <- turb_rdb_fpt_monthly_ml %>% filter(station == "FPT")
min_turb_fpt_ml <- min(monthly_fpt_turb_ml$min)
min_mean_turb_fpt_ml <- min(monthly_fpt_turb_ml$mean)
min_turb_fpt_ml_month <- monthly_fpt_turb_ml %>% filter(min == min_turb_fpt_ml) %>% select(month)
min_mean_turb_fpt_ml_month <- monthly_fpt_turb_ml %>% filter(mean == min_mean_turb_fpt_ml) %>% select(month)

monthly_rdb_turb_ml <- turb_rdb_fpt_monthly_ml %>% filter(station == "RDB")
min_turb_rdb_ml <- min(monthly_rdb_turb_ml$min)
min_mean_turb_rdb_ml <- min(monthly_rdb_turb_ml$mean)
min_turb_rdb_ml_month <- monthly_rdb_turb_ml %>% filter(min == min_turb_rdb_ml) %>% select(month)
min_mean_turb_rdb_ml_month <- monthly_rdb_turb_ml %>% filter(mean == min_mean_turb_rdb_ml) %>% select(month)
```

**Summary**

-   **Red Bluff Diversion Dam:** Minimum turbidity was **`r min_turb_rdb_ml`** FNU and occurred in **`r min_turb_rdb_ml_month`**. The lowest mean turbidity was **`r min_mean_turb_rdb_ml`** FNU and occurred in **`r min_mean_turb_rdb_ml_month`**. 
-   **Sacramento River at Freeport:** Minimum turbidity was **`r min_turb_fpt_ml`** FNU and occurred in **`r min_turb_fpt_ml_month`**. The lowest mean turbidity was **`r min_mean_turb_fpt_ml`** FNU and occurred in **`r min_mean_turb_fpt_ml_month`**. 

#### Water Temperature

```{r WLKwtemp-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Water Temperature (°F) at Sacramento River Below Wilkins Slough (WLK) in September", report_year, "through March", report_year+1, ". Days > 63°F indicates the number of days per month that experienced at least 1 hour where Water Temperature was greater than 63°F.")}

wtemp_wlk_df <- readRDS(paste0("data_raw/wtemp_cdec_WLK_", year(start), "-", year(end2), ".rdsxz")) 
wtemp_wlk_monthly_ml <- f_monthly_extrayear_thresh_greater(wtemp_wlk_df, WaterTemp, 63) %>%
  filter(month_num %in% c(9,10,11,12,1,2,3)) %>%
  select(-month_num)

flextable(wtemp_wlk_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  # hline(i = c(7), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (°F)", max = "Max (°F)", min =  "Min (°F)", flag_days = "Days > 63°F") 
```

```{r echo = FALSE}
monthly_wtemp_wlk_ml <- wtemp_wlk_monthly_ml %>% filter(station == "WLK")
max_wtemp_wlk_ml <- max(monthly_wtemp_wlk_ml$max)
max_mean_wtemp_wlk_ml <- max(monthly_wtemp_wlk_ml$mean)
max_wtemp_exceed_wlk_ml <- max(monthly_wtemp_wlk_ml$flag_days)
max_wtemp_wlk_ml_month <- monthly_wtemp_wlk_ml %>% filter(max == max_wtemp_wlk_ml) %>% select(month)
max_mean_wtemp_wlk_ml_month <- monthly_wtemp_wlk_ml %>% filter(mean == max_mean_wtemp_wlk_ml) %>% select(month)
max_wtemp_exceed_wlk_ml_month <- monthly_wtemp_wlk_ml %>% filter(flag_days == max_wtemp_exceed_wlk_ml) %>% select(month)
```

**Summary**

- Maximum water temperature was **`r max_wtemp_wlk_ml`** degrees F and occurred in **`r max_wtemp_wlk_ml_month`**. The highest mean water temperature was **`r max_mean_wtemp_wlk_ml`** degrees F and occurred in **`r max_mean_wtemp_wlk_ml_month`**.
- The month with greatest days exceeding 63 degrees F (**`r max_wtemp_exceed_wlk_ml`** days) was **`r max_wtemp_exceed_wlk_ml_month`**.

#### Dissolved Oxygen

```{r RDBSRHDO-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("Mean, Maximum, Minimum Monthly Flows (cfs) at Red Bluff Diversion Dam (RDB) and Sacramento River at Hood (SRH) in", report_year, "-", report_year+1, ". Days less than 6 mg/L indicates the number of days per month that experienced at least 1 hour where DO was less than 6 mg/L.")}
do_rdb_srh_df <- readRDS(paste0("data_raw/do_cdec_RDB_SRH_", year(start), "-", year(end2), ".rdsxz")) 
do_rdb_srh_monthly_ml <- f_monthly_extrayear_thresh(do_rdb_srh_df, DO, 6) %>%
  mutate(station = factor(station, levels = c("RDB", "SRH"))) %>%
  filter(month_num %in% c(9,10,11,12,1,2,3)) %>%
  arrange(station) %>%
  select(-month_num)

flextable(do_rdb_srh_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7,14), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)", flag_days = "Days < 6 mg/L") 
```

```{r echo = FALSE}
monthly_do_rdb_ml <- do_rdb_srh_monthly_ml %>% filter(station == "RDB")
min_do_rdb_ml <- min(monthly_do_rdb_ml$min)
min_mean_do_rdb_ml <- min(monthly_do_rdb_ml$mean)
min_do_rdb_ml_month <- monthly_do_rdb_ml %>% filter(min == min_do_rdb_ml) %>% select(month)
min_mean_do_rdb_ml_month <- monthly_do_rdb_ml %>% filter(mean == min_mean_do_rdb_ml) %>% select(month)

monthly_do_srh_ml <- do_rdb_srh_monthly_ml %>% filter(station == "SRH")
min_do_srh_ml <- min(monthly_do_srh_ml$min)
min_mean_do_srh_ml <- min(monthly_do_srh_ml$mean)
min_do_srh_ml_month <- monthly_do_srh_ml %>% filter(min == min_do_srh_ml) %>% select(month)
min_mean_do_srh_ml_month <- monthly_do_srh_ml %>% filter(mean == min_mean_do_srh_ml) %>% select(month)
```

**Summary**

-   **Sacramento River at Bend Bridge:** Minimum dissolved oxygen was **`r min_do_rdb_ml`** mg/L and occurred in **`r min_do_rdb_ml_month[1]`**. The lowest mean dissolved oxygen was **`r min_mean_do_rdb_ml`** mg/L and occurred in **`r min_mean_do_rdb_ml_month`**.
-   **Sacramento River at Hood:** Minimum dissolved oxygen was **`r min_do_srh_ml`** mg/L and occurred in **`r min_do_srh_ml_month[1]`**. The lowest mean dissolved oxygen was **`r min_mean_do_srh_ml`** mg/L and occurred in **`r min_mean_do_srh_ml_month`**.


## Rearing Habitat Capacity 

## Biological Response

Monitoring Sources for abundance, growth/size, migration timing/duration

-   Sac Trawl
-   Tisdale Weir
-   Knights Landing
-   GCID
-   DJFMP
-   Yolo Bypass
-   Chipps Island Trawl (Exit)
-   Genetic (Chipps, SWP/CVP, Knights Landing, Yolo Bypass)

**Data Sources** 

* JPE, Smolt survival from JPE Letters (link)
* 

### Juvenile Production Estimate (Abundance)
```{r}
jpe_all <- read.csv("data_raw/jpe_data.csv")
```

```{r jpe-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Total Natural production entering the Delta (JPE)"}
plot_metric(metric = "Total natural production entering the Delta", fill = "plum4")
```

```{r jpeH-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Total Hatchery Production entering the Delta (Hatchery JPE)"}
plot_metric(metric = "Total LSNFH production entering the Delta")
```

### Smolt Survival 

#### JPE Letter 
Natural-origin smolt survival is calculated at the Tower Bridge from acoustically tagged hatchery fish that are released at RBDD. 


```{r smoltsurvival-fig, fig.cap ="Natural-origin Smolt Survival from RBDD to Tower Bridge. A new calculation method was implemented for BY 2019, resulting in lower estimates. Prior to 2013 a constant value of 0.54 was used."}

df_smoltsurv <- read.csv("data_raw/jpe_data.csv") %>%
  filter(component %in% c("Estimated smolt survival term", "Fry-to-smolt survival"),
          brood_year <= report_year,
          brood_year > 2012) 

smoltsurv_avg10 <- df_smoltsurv %>% filter(brood_year > report_year-10)
  
ggplot() + 
  geom_col(data = df_smoltsurv, aes(brood_year, value, fill = component), position = "dodge") +
  geom_segment(data = smoltsurv_avg10 %>% filter(component == "Estimated smolt survival term"), aes(x= min(brood_year)-0.4, xend = max(brood_year)+0.4, y = mean(value, na.rm = TRUE)), linetype = "dashed") + 
  geom_segment(data = smoltsurv_avg10 %>% filter(component == "Fry-to-smolt survival"), aes(x= min(brood_year)-0.4, xend = max(brood_year)+0.4, y = mean(value, na.rm = TRUE)), linetype = "dotted") + 
    # geom_text(data = df_metric, aes(x = brood_year, y = value, label = round(value,2)))+
  labs(x = "Brood Year", y = "Survival")+
  scale_fill_manual(values = c("steelblue4", "goldenrod2")) +
  scale_x_continuous(breaks = seq(2002, report_year, by = 1)) +
  theme_bw()
```
#### Acoustic Tagging

Reach-specific survival 

```{r hatchery-tab, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Table of Hatchery WR Juvenile Survival." }
hatchery_release <- read_csv("data_raw/hatchery_release_data.csv") %>%
  mutate(rel_date = factor(rel_date))

hatchery_table <- hatchery_release %>%
  mutate(ReachSurvival = paste0(reach_survival_est, " (", LCL_reach, ", ", UCL_reach, ")"),
         CumulativeSurvival = paste0(cumulative_survival_est, " (", LCL_cum, ", ", UCL_cum, ")"),
         rkm_start = round(rkm_start)) %>%
  select(rel_date, reach_start, reach_end, rkm_start, ReachSurvival, CumulativeSurvival, count)

flextable(hatchery_table)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  # hline(i = c(7,14), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  # colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(CumulativeSurvival = "Cumulative Survival", ReachSurvival = "Reach Survival", rkm_start = "River Kilometer", rel_date = "Release Date")
```

### Migration Timing 

Cumulative Raw Catch: RBDD, Chipps, Tisdale, Knights, Sac Beach Seines, Sac Trawls
```{r juvtiming-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap ="Raw Juvenile Rotary Screw Trap Cumulative Catch"}
juv_ml <- read_csv("data_raw/cohort_juv_data.csv") %>%
  filter(year(ymd(Date)) >= report_year)%>%
  mutate(Date = lubridate::ymd(Date)) %>%
  janitor::clean_names() %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  select(date, 
         `Tisdale Weir RST` = cumulative_raw_tisdale_weir_rst,
         `Knights Landing RST` = cumulative_raw_knights_landing_rst,
         `Lower Feather RST` = cumulative_raw_lower_feather_rst,
         `Lower Sac RST` = cumulative_raw_lower_sacramento_rst,
         `Sac Beach Seines` = cumulative_raw_sacramento_beach_seines_sr080e_sr071e_sr062e_sr057e_sr055e_sr060e_am001s_sr049e,
         `Sac Trawls` = cumulative_raw_sacramento_trawls_sr055m_sr055e_sr055w_sr055x,
         `Chipps Island Trawls` = cumulative_raw_chipps_island_trawls_sb018m_sb018n_sb018s_sb018x,
         `RBDD Daily` = red_bluff_diversion_dam_daily_estimates)

juv_ml_long <- juv_ml %>%
  tidyr::pivot_longer(cols = 2:9, names_to = "Survey", values_to = "Catch") %>%
  mutate(separate = if_else(Survey == "RBDD Daily",  "Red Bluff Diversion Dam", "Other Rotary Screw Traps"),
         separate = factor(separate, levels = c("Red Bluff Diversion Dam", "Other Rotary Screw Traps"))) %>%
  filter(!(Survey == "RBDD Daily" & Catch==0 & date>as.Date("2021-10-01"))) 
  

ggplot(juv_ml_long) +
  geom_point(aes(x = date, y = Catch, color = Survey, shape = Survey), size = 1) +
  facet_wrap(~separate, scales= "free_y", nrow = 2)+
  scale_x_date(date_breaks = "1 month", date_labels = "%b-%Y") +
  scale_shape_manual(values = c(0, 16, 2, 3, 25, 17, 23, 11))+
  scale_color_viridis(discrete = TRUE) + 
  labs(y = "Cumulative Raw Catch")+
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90),
        axis.title.x = element_blank())
```

Median Passage Dates
```{r}

```

Migration Timing
```{r}

```


### Condition

Do we want FL on any surveys?
