# Sacramento-San Joaquin Delta Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Sacramento-San Joaquin Delta.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)
library(flextable)
library(CDECRetrieve)
source("functions.R")
source("parameters.R")
```

## Habitat Attributes

1. Rearing Habitat Capacity (Floodplain Connectivity)

* Weir overtopping

2. Entrainment Risk

3. Food Availability

## Environmental Drivers

### Sacramento River Flow and Delta Outflow

```{r deltaflow-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("FPT (Sacramento River at Freeport), Delta Outflow (DTO), OMR (OMR) Mean, Maximum, Minimum Monthly Flows (cfs) in", report_year, "-", report_year+1)}
flow_fpt_monthly <- readRDS(paste0("data_raw/flow_fpt_monthly_", year(start), "-", year(end2), ".rds")) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5, 6))
flow_OMR_monthly <- readRDS(paste0("data_raw/omr_OMR_monthly_", year(start), "-", year(end2), ".rds")) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5, 6))
outflow_monthly <- readRDS(paste0("data_raw/outflow_monthly_", year(start), "-", year(end2), ".rds")) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5, 6))

flow_delta_monthly <- rbind(flow_fpt_monthly, outflow_monthly,flow_OMR_monthly) %>%
  select(-month_num)

flextable(flow_delta_monthly)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7, 14, 21), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)", flag_days = "Days < 6 mg/L") 

```


```{r FPTflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Freeport (FPT) Average Flows (cfs) in",report_year, "and over the 10-year average"), fig.width = 6, fig.height = 5}
flow_fpt <- readRDS(paste0("data_raw/flow_fpt_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(12, 1, 2, 3, 4, 5, 6))

ggplot(flow_fpt) + 
  geom_line(aes(date, flow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots 
```
```{r DTOflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Delta Outflow (DTO) in",report_year, "and over the 10-year average"), fig.width = 6, fig.height = 5}
outflow<- readRDS(paste0("data_raw/outflow_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(12, 1, 2, 3, 4, 5, 6))

ggplot(outflow) + 
  geom_line(aes(date, Outflow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots 
```
```{r OMRflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("OMR Flow (OMR) (cfs) in",report_year, "and over the 10-year average"), fig.width = 6, fig.height = 5}
omr<- readRDS(paste0("data_raw/omr_OMR_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(12, 1, 2, 3, 4, 5, 6))

(omr_plot <- ggplot(omr) + 
  geom_line(aes(date, omr, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots )

plotly::ggplotly(omr_plot) %>%
  layout(legend = list(orientation = "h"))
```

### Water Temperature

```{r FPTSUSSWEGSSMALwtemp-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("FPT (Sacramento River at Freeport), SUS (Steamboat Slough below Sutter Slough), SWE (Sacramento River at Walnut Grove), GSS (Georgiana Slough at Sacramento River), MAL (Sacramento River at Mallard Island) Mean, Maximum, Minimum Monthly Water Temperature (°F) in", report_year, "-", report_year+1)}
wtemp_delta_df <- readRDS(paste0("data_raw/wtemp_cdec_FPT_SUS_SWE_GSS_MAL_", year(start), "-", year(end2), ".rdsxz")) 

wtemp_delta_monthly_ml <- f_monthly_extrayear_thresh_greater(wtemp_delta_df, WaterTemp, 63) %>%
  mutate(station = factor(station, levels = c("FPT", "SUS", "SWE", "GSS" ,"MAL"))) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5,6)) %>%
  select(-month_num) %>%
  arrange(station) 
  
flextable(wtemp_delta_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7, 14, 21, 28), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (°F)", max = "Max (°F)", min =  "Min (°F)", flag_days = "Days > 63°F") 
```


### Dissolved Oxygen

```{r SRHSXSBLPMALDO-tab, echo = FALSE, message = FALSE, warning = FALSE, tab.cap = paste("SRH (Sacramento River at Hood), SXS (Steamboat Slough near Sacramento River), BLP (Blind Point), MAL (Sacramento River at Mallard Island) Mean, Maximum, Minimum Monthly DO (mg/L) in", report_year, "-", report_year+1)}
do_srh_sxs_blp_mal_df <- readRDS(paste0("data_raw/do_cdec_SRH_SXS_BLP_MAL_", year(start), "-", year(end2), ".rdsxz")) 

do_srh_sxs_blp_mal_monthly_ml <- f_monthly_extrayear_thresh(do_srh_sxs_blp_mal_df, DO, 6) %>%
  mutate(station = factor(station, levels = c("SRH", "SXS", "BLP", "MAL"))) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5,6)) %>%
  select(-month_num) %>%
  arrange(station) 
  
flextable(do_srh_sxs_blp_mal_monthly_ml)%>%
  add_footer_lines() %>%
  add_header_lines() %>%
  width(width = 1, unit = "in") %>%
  hline(i = c(7, 14, 21, 28), part = 'body') %>%
  vline()%>%
  border_outer() %>%
  bold(part = "header") %>%
  colformat_num(j = "year", big.mark = "") %>%
  set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (cfs)", max = "Max (cfs)", min =  "Min (cfs)", flag_days = "Days < 6 mg/L") 
```



## Biological Response

Monitoring Sources for abundance, growth/size, migration timing/duration

* Sac Trawl
* Tisdale Weir
* Knights Landing
* GCID
* DJFMP
* Yolo Bypass
* Chipps Island Trawl (Exit)
* Genetic (Chipps, SWP/CVP, Knights Landing, Yolo Bypass)

1. Abundance (Count) (IEP Monitoring)

2. Condition (IEP Monitoring)

* FL

3. Migration Timing (IEP Monitoring)

* SacPAS style plots of historical and current year?

*Chipps Trawl Timing*

*Sac Trawl Timing*

*Sac Beach Seine Timing*


4. Migration Duration

* Calfish Track/ERDDAP

5. Migration Routing

6. Survival 

* Hatchery real-time: Calfish Track/ERDDAP
* Natural Origin Smolt survival (O Farell et al. 2018)
* Hatchery Origin Smolt survival
* Modeled:
  ** Juvenile: STARS
  ** Fish Model
* Survival to Delta: Production (Hatchery JPE, Modeled JPE)

7. Loss and Salvage (Salvage)

* Take Limit
* Model


