# Sacramento-San Joaquin Delta Juveniles

This section describes environmental attributes associated with and responses during the out-migrating juvenile life stage in the Sacramento-San Joaquin Delta.

```{r setup5, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(viridis)
library(sharpshootR)
library(plotly)
library(here)
library(readr)
library(ggridges)

library(kableExtra)
library(flextable)
source("functions.R")
source("parameters.R")
```

---

## Habitat Attributes

1.  Rearing Habitat Capacity (Floodplain Connectivity)

-   Weir overtopping

---


### Food Availability

```{r meso-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Zooplankton Abundance in the Delta, December ", report_year, "-", "June ", report_year+1, " and 10-year average CPUE")}

mesos <- read_csv("data_raw/zooper_meso.csv") %>%
  filter(!is.na(Region)) %>%
 mutate(Month_fac = factor(Month_fac,
                    levels = c("Dec", "Jan", "Feb", "Mar", "Apr","May", "Jun")),
        Region= factor(Region, levels = c("Far West", "West", "North", "South")))

ggplot(mesos) + 
  geom_col(aes(Month_fac, meanCPUE, fill = Year_type), position = position_dodge(), width = 0.6) + theme_bw() + 
  labs(y= "CPUE", x= "Month") + 
  scale_fill_manual(values = c("goldenrod3", "gray70"))+
  facet_grid(Region~Order, scales = "free_y") +
  theme_bw() + 
  theme(legend.position = "top")
```

Macrozooplankton currently lacking 2022 data

```{r macro-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Amphipod and Mysid Abundance in the Delta, December ", report_year, "-", "June " , report_year+1, " and 10-year average CPUE")}

macros <- read_csv("data_raw/zooper_macro.csv") %>%
  filter(!is.na(Region)) %>%
 mutate(Month_fac = factor(Month_fac,
                    levels = c("Dec", "Jan", "Feb", "Mar", "Apr","May", "Jun")),
        Region= factor(Region, levels = c("Far West", "West", "North", "South")))

ggplot(macros) + 
  geom_col(aes(Month_fac, meanCPUE, fill = Year_type), position = position_dodge(), width = 0.6) + theme_bw() + 
  labs(y= "CPUE", x= "Month") + 
  scale_fill_manual(values = c("goldenrod3", "gray70"))+
  facet_grid(Region~Order, scales = "free_y")+
  theme_bw() + 
  theme(legend.position = "top")
```

---

## Environmental Drivers

---

### Sacramento River Flow and Delta Outflow

```{r deltaflow-tab}
flow_fpt_monthly <- readRDS(paste0("data_raw/flow_fpt_monthly_", year(start), "-", year(end2), ".rds")) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5, 6))
flow_OMR_monthly <- readRDS(paste0("data_raw/omr_OMR_monthly_", year(start), "-", year(end2), ".rds")) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5, 6))
outflow_monthly <- readRDS(paste0("data_raw/outflow_monthly_", year(start), "-", year(end2), ".rds")) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5, 6))

flow_delta_monthly <- rbind(flow_fpt_monthly, outflow_monthly,flow_OMR_monthly) %>%
  select(-month_num)

flow_delta_monthly_t <- flow_delta_monthly

colnames(flow_delta_monthly_t) <- stringr::str_to_title(colnames(flow_delta_monthly_t))

kable(flow_delta_monthly_t,
      label = NA,
      vline = "",
      caption = paste("Sacramento River at Freeport (FPT), Delta Outflow (DTO), Old and Middle River (OMR) Mean, Maximum, Minimum Monthly Flows (cfs) in", report_year, "-", report_year+1),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(c(7,14,21),extra_css = "border-bottom: 1px solid;")


```

```{r FPTflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Freeport (FPT) Average Flows (cfs) in",report_year, "and over the 10-year average"), fig.width = 8, fig.height = 4.5}
flow_fpt <- readRDS(paste0("data_raw/flow_fpt_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(12, 1, 2, 3, 4, 5, 6))

ggplotly(ggplot(flow_fpt) + 
  geom_line(aes(date, flow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots )
```

```{r DTOflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("Delta Outflow (DTO) in",report_year, "and over the 10-year average"), fig.width = 8, fig.height = 4.5}
outflow<- readRDS(paste0("data_raw/outflow_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(12, 1, 2, 3, 4, 5, 6))

ggplotly(ggplot(outflow) + 
  geom_line(aes(date, Outflow, color = plot_year, linetype = plot_year)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots )
```

```{r OMRflow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = paste("OMR Flow (OMR) (cfs) in",report_year, "and over the 10-year average"), fig.width = 8, fig.height = 4.5}
omr<- readRDS(paste0("data_raw/omr_OMR_plot_data_", year(start), "-", year(end2), ".rds")) %>%
  filter(month %in% c(12, 1, 2, 3, 4, 5, 6))

ggplotly(ggplot(omr) + 
  geom_line(aes(date, omr, color = plot_year, linetype = plot_year)) +
   geom_hline(yintercept = 0, linetype = "dotted") + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
  scale_color_manual(values = c("black", "steelblue")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  facet_wrap(~station, nrow = 2) + 
  labs(y = "Flow (cfs)") +
  theme_plots )

# plotly::ggplotly(omr_plot) %>%
#   layout(legend = list(orientation = "h"))
```

```{r calculate_env_juv_delta,echo = FALSE}
monthly_fpt <- flow_delta_monthly %>% filter(station == "FPT")
max_flow_fpt <- max(monthly_fpt$max)
max_mean_flow_fpt <- max(monthly_fpt$mean)
max_flow_fpt_month <- monthly_fpt %>% filter(max == max_flow_fpt) %>% select(month)
max_mean_flow_fpt_month <- monthly_fpt %>% filter(mean == max_mean_flow_fpt) %>% select(month)

monthly_dto <- flow_delta_monthly %>% filter(station == "DTO")
max_flow_dto <- max(monthly_dto$max)
max_mean_flow_dto <- max(monthly_dto$mean)
max_flow_dto_month <- monthly_dto %>% filter(max == max_flow_dto) %>% select(month)
max_mean_flow_dto_month <- monthly_dto %>% filter(mean == max_mean_flow_dto) %>% select(month)

monthly_omr <- flow_delta_monthly %>% filter(station == "OMR") 
min_flow_omr <- min(monthly_omr$min)
min_mean_flow_omr <- min(monthly_omr$mean)
min_flow_omr_month <- monthly_omr %>% filter(min == min_flow_omr) %>% select(month)
min_mean_flow_omr_month <- monthly_omr %>% filter(mean == min_mean_flow_omr) %>% select(month)
```

**Summary**

-   **Sacramento River at Freeport:** Peak flows were **`r max_flow_fpt`** cfs and occurred in **`r max_flow_fpt_month[1]`**. The highest mean flows were **`r max_mean_flow_fpt`** cfs and occurred in **`r max_mean_flow_fpt_month`**. Flow was generally lower than average.

-   **Delta Outflow:** Peak Delta outflow was **`r max_flow_dto`** cfs and occurred in **`r max_flow_dto_month[1]`**. The highest mean Delta outflow was **`r max_mean_flow_dto`** cfs and occurred in **`r max_mean_flow_dto_month`**. Flow was generally lower than average.

-   **OMR:** The most negative OMR flows were **`r min_flow_omr`** cfs and occurred in **`r min_flow_omr_month[1]`**. The most negative mean OMR flows were **`r min_mean_flow_omr`** cfs and occurred in **`r min_mean_flow_omr_month`**. OMR was generally similar to average.

---

### Water Temperature

```{r FPTSUSSWEGSSMALwtemp-tab}
wtemp_delta_df <- readRDS(paste0("data_raw/wtemp_cdec_FPT_SUS_SWE_GSS_MAL_", year(start), "-", year(end2), ".rdsxz")) 

wtemp_delta_monthly <- f_monthly_extrayear_thresh_greater(wtemp_delta_df, WaterTemp, 63) %>%
  mutate(station = factor(station, levels = c("FPT", "SUS", "SWE", "GSS" ,"MAL"))) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5,6)) %>%
  select(-month_num) %>%
  arrange(station) 

wtemp_delta_monthly_t <- wtemp_delta_monthly %>%
  rename("Days < 63 degF" = flag_days)

colnames(wtemp_delta_monthly_t) <- stringr::str_to_title(colnames(wtemp_delta_monthly_t))

kable(wtemp_delta_monthly_t,
      label = NA,
      vline = "",
      caption = paste("FPT (Sacramento River at Freeport), SUS (Steamboat Slough below Sutter Slough), SWE (Sacramento River at Walnut Grove), GSS (Georgiana Slough at Sacramento River), MAL (Sacramento River at Mallard Island) Mean, Maximum, Minimum Monthly Water Temperature (°F) in", report_year, "-", report_year+1),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(c(7,14,21,28),extra_css = "border-bottom: 1px solid;")

# flextable(wtemp_delta_monthly)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = c(7, 14, 21, 28), part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (°F)", max = "Max (°F)", min =  "Min (°F)", flag_days = "Days > 63°F") 
```

```{r calculate_temps_juv_delta, echo = FALSE}
monthly_wtemp_fpt_delta <- wtemp_delta_monthly %>% filter(station == "FPT")
max_wtemp_fpt_delta <- max(monthly_wtemp_fpt_delta$max)
max_mean_wtemp_fpt_delta <- max(monthly_wtemp_fpt_delta$mean)
max_wtemp_fpt_delta_month <- monthly_wtemp_fpt_delta %>% filter(max == max_wtemp_fpt_delta) %>% select(month)
max_mean_wtemp_fpt_delta_month <- monthly_wtemp_fpt_delta %>% filter(mean == max_mean_wtemp_fpt_delta) %>% select(month)

monthly_wtemp_sus_delta <- wtemp_delta_monthly %>% filter(station == "SUS")
max_wtemp_sus_delta <- max(monthly_wtemp_sus_delta$max)
max_mean_wtemp_sus_delta <- max(monthly_wtemp_sus_delta$mean)
max_wtemp_sus_delta_month <- monthly_wtemp_sus_delta %>% filter(max == max_wtemp_sus_delta) %>% select(month)
max_mean_wtemp_sus_delta_month <- monthly_wtemp_sus_delta %>% filter(mean == max_mean_wtemp_sus_delta) %>% select(month)

monthly_wtemp_gss_delta <- wtemp_delta_monthly %>% filter(station == "GSS")
max_wtemp_gss_delta <- max(monthly_wtemp_gss_delta$max)
max_mean_wtemp_gss_delta <- max(monthly_wtemp_gss_delta$mean)
max_wtemp_gss_delta_month <- monthly_wtemp_gss_delta %>% filter(max == max_wtemp_gss_delta) %>% select(month)
max_mean_wtemp_gss_delta_month <- monthly_wtemp_gss_delta %>% filter(mean == max_mean_wtemp_gss_delta) %>% select(month)

monthly_wtemp_mal_delta <- wtemp_delta_monthly %>% filter(station == "MAL")
max_wtemp_mal_delta <- max(monthly_wtemp_mal_delta$max)
max_mean_wtemp_mal_delta <- max(monthly_wtemp_mal_delta$mean)
max_wtemp_mal_delta_month <- monthly_wtemp_mal_delta %>% filter(max == max_wtemp_mal_delta) %>% select(month)
max_mean_wtemp_mal_delta_month <- monthly_wtemp_mal_delta %>% filter(mean == max_mean_wtemp_mal_delta) %>% select(month)
```

**Summary**

-   Maximum water temperature was **`r max_wtemp_fpt_delta`** degrees F and occurred in **`r max_wtemp_fpt_delta_month`**. The highest mean water temperature was **`r max_mean_wtemp_fpt_delta`** degrees F and occurred in **`r max_mean_wtemp_fpt_delta_month`**.
-   Maximum water temperature was **`r max_wtemp_sus_delta`** degrees F and occurred in **`r max_wtemp_sus_delta_month`**. The highest mean water temperature was **`r max_mean_wtemp_sus_delta`** degrees F and occurred in **`r max_mean_wtemp_sus_delta_month`**.
-   Maximum water temperature was **`r max_wtemp_gss_delta`** degrees F and occurred in **`r max_wtemp_gss_delta_month`**. The highest mean water temperature was **`r max_mean_wtemp_gss_delta`** degrees F and occurred in **`r max_mean_wtemp_gss_delta_month`**.
-   Maximum water temperature was **`r max_wtemp_mal_delta`** degrees F and occurred in **`r max_wtemp_mal_delta_month`**. The highest mean water temperature was **`r max_mean_wtemp_mal_delta`** degrees F and occurred in **`r max_mean_wtemp_mal_delta_month`**.

---

### Dissolved Oxygen

```{r SRHSXSBLPMALDO-tab}
do_delta_df <- readRDS(paste0("data_raw/do_cdec_SRH_SXS_BLP_MAL_", year(start), "-", year(end2), ".rdsxz")) 

do_delta_monthly <- f_monthly_extrayear_thresh(do_delta_df, DO, 6) %>%
  mutate(station = factor(station, levels = c("SRH", "SXS", "BLP", "MAL"))) %>%
  filter(month_num %in% c(12, 1, 2, 3, 4, 5,6)) %>%
  select(-month_num) %>%
  arrange(station) 

do_delta_monthly_t <- do_delta_monthly %>%
  rename("Days < 6 mg/L" = flag_days)

colnames(do_delta_monthly_t) <- stringr::str_to_title(colnames(do_delta_monthly_t))

kable(do_delta_monthly_t,
      label = NA,
      vline = "",
      caption = paste("SRH (Sacramento River at Hood), SXS (Steamboat Slough near Sacramento River), BLP (Blind Point), MAL (Sacramento River at Mallard Island) Mean, Maximum, Minimum Monthly DO (mg/L) in", report_year, "-", report_year+1),
      valign = "t") %>%
  kable_classic(html_font = "Cambria") %>%
      row_spec(c(7,14,21,28),extra_css = "border-bottom: 1px solid;")


  
# flextable(do_delta_monthly)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = c(7, 14, 21, 28), part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(year = "Year", month = "Month", station = "Station", mean = "Mean (mg/L)", max = "Max (mg/L)", min =  "Min (mg/L)", flag_days = "Days < 6 mg/L") 
```

```{r calculate_do_juv_delta, echo = FALSE}
monthly_do_srh_delta <- do_delta_monthly %>% filter(station == "SRH")
max_do_srh_delta <- max(monthly_do_srh_delta$max)
max_mean_do_srh_delta <- max(monthly_do_srh_delta$mean)
max_do_srh_delta_month <- monthly_do_srh_delta %>% filter(max == max_do_srh_delta) %>% select(month)
max_mean_do_srh_delta_month <- monthly_do_srh_delta %>% filter(mean == max_mean_do_srh_delta) %>% select(month)

monthly_do_sxs_delta <- do_delta_monthly %>% filter(station == "SXS")
max_do_sxs_delta <- max(monthly_do_sxs_delta$max)
max_mean_do_sxs_delta <- max(monthly_do_sxs_delta$mean)
max_do_sxs_delta_month <- monthly_do_sxs_delta %>% filter(max == max_do_sxs_delta) %>% select(month)
max_mean_do_sxs_delta_month <- monthly_do_sxs_delta %>% filter(mean == max_mean_do_sxs_delta) %>% select(month)

monthly_do_blp_delta <- do_delta_monthly %>% filter(station == "BLP")
max_do_blp_delta <- max(monthly_do_blp_delta$max)
max_mean_do_blp_delta <- max(monthly_do_blp_delta$mean)
max_do_blp_delta_month <- monthly_do_blp_delta %>% filter(max == max_do_blp_delta) %>% select(month)
max_mean_do_blp_delta_month <- monthly_do_blp_delta %>% filter(mean == max_mean_do_blp_delta) %>% select(month)

monthly_do_mal_delta <- do_delta_monthly %>% filter(station == "MAL")
max_do_mal_delta <- max(monthly_do_mal_delta$max)
max_mean_do_mal_delta <- max(monthly_do_mal_delta$mean)
max_do_mal_delta_month <- monthly_do_mal_delta %>% filter(max == max_do_mal_delta) %>% select(month)
max_mean_do_mal_delta_month <- monthly_do_mal_delta %>% filter(mean == max_mean_do_mal_delta) %>% select(month)
```

**Summary**

-   Maximum water temperature was **`r max_do_srh_delta`** degrees F and occurred in **`r max_do_srh_delta_month`**. The highest mean water temperature was **`r max_mean_do_srh_delta`** degrees F and occurred in **`r max_mean_do_srh_delta_month`**.
-   Maximum water temperature was **`r max_do_sxs_delta`** degrees F and occurred in **`r max_do_sxs_delta_month[1,]`** and **`r max_do_sxs_delta_month[2,]`**. The highest mean water temperature was **`r max_mean_do_sxs_delta`** degrees F and occurred in **`r max_mean_do_sxs_delta_month`**.
-   Maximum water temperature was **`r max_do_blp_delta`** degrees F and occurred in **`r max_do_blp_delta_month`**. The highest mean water temperature was **`r max_mean_do_blp_delta`** degrees F and occurred in **`r max_mean_do_blp_delta_month`**.
-   Maximum water temperature was **`r max_do_mal_delta`** degrees F and occurred in **`r max_do_mal_delta_month`**. The highest mean water temperature was **`r max_mean_do_mal_delta`** degrees F and occurred in **`r max_mean_do_mal_delta_month`**.

---

## Biological Response

---

### Survival

```{r hatcherydelta-tab}
hatchery_release <- read_csv("data_raw/hatchery_release_data.csv") %>%
  mutate(rel_date = factor(rel_date)) %>%
  filter(!is.na(reach_start))

hatchery_table_delta <- hatchery_release %>%
  filter(rkm_start <=222,!is.na(reach_start)) %>%
  mutate(ReachSurvival = paste0(reach_survival_est, " (", LCL_reach, ", ", UCL_reach, ")"),
         CumulativeSurvival = paste0(cumulative_survival_est, " (", LCL_cum, ", ", UCL_cum, ")"),
         rkm_start = round(rkm_start)) %>%
  select(rel_date, reach_start, reach_end, rkm_start, ReachSurvival, CumulativeSurvival, count)

kable(hatchery_table_delta,
      label = NA,
      vline = "",
      caption = "Table of Hatchery WR Juvenile Survival",
      valign = "t") %>%
  kable_classic(html_font = "Cambria") 

# flextable(hatchery_table_delta)%>%
#   add_footer_lines() %>%
#   add_header_lines() %>%
#   width(width = 1, unit = "in") %>%
#   hline(i = 9, part = 'body') %>%
#   vline()%>%
#   border_outer() %>%
#   bold(part = "header") %>%
#   # colformat_num(j = "year", big.mark = "") %>%
#   set_header_labels(CumulativeSurvival = "Cumulative Survival", ReachSurvival = "Reach Survival", rkm_start = "River Kilometer", rel_date = "Release Date")
```

```{r hatcherysurvival-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap ="Cumulative Survival by River Kilometer"}

plotly::ggplotly(ggplot(hatchery_release) +
  geom_point(aes(x = rkm_start, y =cumulative_survival_est, color = rel_date,
                 text = paste("Reach End:", reach_end))) +
  geom_errorbar(aes(x = rkm_start,ymin = LCL_cum, ymax = UCL_cum,  color = rel_date))  +
  geom_line(aes(x = rkm_start, y = cumulative_survival_est, color = rel_date))+
  # facet_wrap(~rel_date, nrow = 2) + 
  scale_x_continuous(trans = "reverse", breaks = seq(0, 560, by = 50)) +
  scale_color_manual(values = c("steelblue4", "chartreuse3"))+
  labs(y = "Cumulative Survival", x = "River Kilometer", color = "Release Date") +
  theme_bw())

```

---

### Abundance

Catch for all surveys

```{r catch_surveys, echo = FALSE}
index <- read_csv("data_raw/cohort_juv_index_data_cumulative_currentyear_long.csv")
abund_delta_surveys <-  index %>%
  group_by(Survey) %>%
  summarize(Abund = max(Catch))

juvdates <- read_csv("data_raw/cohort_juv_data_cumulative_currentyear.csv")
delta_entry_first <- format(juvdates$date[match(FALSE, cummax(juvdates$`Sac Trawls`) == 0)], "%B %d, %Y")
delta_entry_median <- format(juvdates$date[match(TRUE, juvdates$`Sac Trawls`== median(juvdates$`Sac Trawls`))], "%B %d, %Y")
delta_entry_last <- format(juvdates$date[match(TRUE, juvdates$`Sac Trawls`== max(juvdates$`Sac Trawls`))], "%B %d, %Y")
delta_exit_first <- format(juvdates$date[match(FALSE, cummax(juvdates$`Chipps Island Trawls`) == 0)], "%B %d, %Y")
delta_exit_median <- format(juvdates$date[match(TRUE, juvdates$`Chipps Island Trawls`== median(juvdates$`Chipps Island Trawls`))], "%B %d, %Y")
delta_exit_last <- format(juvdates$date[match(TRUE, juvdates$`Chipps Island Trawls`== max(juvdates$`Chipps Island Trawls`))], "%B %d, %Y")
```

**Summary**

-   Juvenile WRCS cumulative total catch: 
    - Sacramento Trawls at Sherwood Harbor: **`r abund_delta_surveys$Abund[abund_delta_surveys$Survey == "Sac Trawls"]`** (Index = **`r abund_delta_surveys$Abund[abund_delta_surveys$Survey == "Sac Trawls Index"]`**)
    - Sacramento Beach Seines: **`r abund_delta_surveys$Abund[abund_delta_surveys$Survey == "Sac Beach Seines"]`** (Index = **`r abund_delta_surveys$Abund[abund_delta_surveys$Survey == "Sac Beach Seines Index"]`**)
    - Chipps Island Trawl: **`r abund_delta_surveys$Abund[abund_delta_surveys$Survey == "Chipps Island Trawls"]`**
-   Migration Timing: 
    - Delta Entry (Sacramento Trawls at Sherwood Harbor): 
      - First: **`r delta_entry_first`**    
      - Median: **`r delta_entry_median`**
      - Last: **`r delta_entry_last`**
    - Delta Exit (Chipps Island Trawl): 
      - First: **`r delta_exit_first`**    
      - Median: **`r delta_exit_median`**
      - Last: **`r delta_exit_last`**

---

### Migration Timing

Sac Trawl Data (Raw Catch by Day or Week?)

SacPAS Migration Timing Table - LAD Median Dates, 10 Year Comparison Sacramento Beach Seines, Trawls, Chipps Island Trawls


```{r}
chipps_link <- paste0("https://www.cbr.washington.edu/sacramento/data/php/rpt/hrt.php?species=CHN%3AWinter&loc=SB018&years=10&typeData=index&histYear=",report_year,"&outputFormat=hrtplotOnly")

download.file(url = chipps_link,
              destfile = paste0(figures_folder, "migtiming",report_year,"_chipps.png"),
              mode="wb")
```


```{r chipps-timing-fig,fig.cap = "Delta Exit (Chipps Island) Migration Timing", out.width = "150%"}
knitr::include_graphics(here(paste0(figures_folder,"migtiming",report_year,
                                    "_chipps.png")))
```

---

### STARS Survival and Routing
```{r survival-routing-data, echo = FALSE}
year_specific_data <- read_csv("data_raw/STARS_data.csv")
```

```{r survival-fig}
# Define colors for each route
colors <- c("Overall" = "black", "Yolo" = "lightblue", "Sutter" = "blue", "Steamboat" = "purple", "Sacramento" = "darkgrey", "Interior Delta" = "orange")

(survival_plot <- year_specific_data %>%
  dplyr::filter(metric == "Survival",
                !(lubridate::month(date) %in% c(6,7,8))) %>%
  group_by(route) %>%
  ggplot(aes(x = date)) +
  geom_ribbon( aes(ymin = lowerCI, ymax = upperCI,  fill = route), alpha = .1) +
  geom_line(aes(y = median, color = route), size = 1) +
  labs(x = 'Month',
       y = 'Apparent survival probability',
       subtitle = "Delta STARS Model -\nPredicted Natural Winter-run Chinook Daily Cohorts Passage, Knights Landing to Chipps Island",
       title = paste0("WY", report_year, " Survival: Median survival of daily cohorts by route"),
       caption = paste0("Data source: Delta STARS developed by USGS Quantitative Fisheries Ecology Section and deployed by SacPAS."),
       color = "Route survival,\nmedian with 80% CI",
       fill = "Route survival,\nmedian with 80% CI") +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(
    text = element_text(size = 15),
    panel.grid.major = element_line(linetype = "dotted"),
    panel.border = element_rect(colour = "black", fill = NA, size = .5),
    axis.ticks = element_line(size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank()
  ))

```

```{r routing-fig}
(route_probability_plot <- year_specific_data %>%
  dplyr::filter(metric == "Routing Probability",
                !(lubridate::month(date) %in% c(6,7,8))) %>%
  group_by(route) %>%
  ggplot(aes(x = date)) +
  geom_ribbon( aes(ymin = lowerCI, ymax = upperCI,  fill = route), alpha = .1) +
  geom_line(aes(y = median, color = route), size = 0.9) +
  labs(x = 'Month',
       y = 'Routing Probability',
       subtitle = "Delta STARS Model -\nPredicted Natural Winter-run Chinook Daily Cohorts Passage, Knights Landing to Chipps Island",
       title = paste0("WY",report_year, " Route-specific probability: Proportion of daily cohorts using a specific route"),
       caption = paste0("Data source: Delta STARS developed by USGS Quantitative Fisheries Ecology Section and deployed by SacPAS.\n"),
       color = "Route probability,\nmedian with 80% CI",
       fill = "Route probability,\nmedian with 80% CI") +
  scale_y_continuous( expand = c(0,0)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(
    text = element_text(size = 15),
    panel.grid.major = element_line(linetype = "dotted"),
    panel.border = element_rect(colour = "black", fill = NA, size = .5),
    axis.ticks = element_line(size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank()

  ))
```

---

### Condition

Plot of current year sizes for Salvage, Chipps, Sacramento Beach Seines, Sac Trawls at Sherwood

```{r}

```

```{r salvage_fl-fig, fig.cap = "Fork Lengths of Genetic and LAD Winter Run Chinook Salmon Juveniles at Salvage. Points indicate median fork length."}
salvage_wr <- read_csv("data_raw/salvage_allyears.csv") %>%
  mutate(WY = if_else(Month > 9, Year + 1, Year)) %>%
  filter(Length <750, 
         Adipose.Clip == "Unclipped") %>%
  mutate(Race = LAD.Race, 
         RaceType = "LAD") 

salvage_dna_wr <- salvage_wr %>%
  filter(DNA.Race == "Winter") %>%
  mutate(Race = DNA.Race, 
         RaceType = "DNA")

salvage_wr_all <- bind_rows(salvage_wr, salvage_dna_wr) %>% filter(!is.na(RaceType)) %>%
  filter(WY <= report_year)

median_salvage_fl <- salvage_wr_all %>% group_by(WY, RaceType) %>%
  summarize(Length = median(Length))

ggplot() +
  geom_density_ridges(data = salvage_wr_all, aes(x = Length, y = factor(WY), fill = RaceType), scale = 1.5, draw_baseline = FALSE) +
  geom_point(data = median_salvage_fl, aes(x = Length, y = factor(WY)), shape = 21)+
  labs(x = 'Fork Length (mm)', y = 'Water Year') +
  facet_wrap(~RaceType) + 
  theme_bw() +
  theme(legend.position = 'none',
        plot.margin = ggplot2::margin(0.5,0.5,0.25,0.25, unit = 'cm'),
        axis.title.x = element_text(margin=ggplot2::margin(t=10)),
        axis.title.y = element_text(margin=ggplot2::margin(r=10)))
```

```{r chipps_fl-fig, fig.cap = "Fork Lengths of Genetic and LAD Winter Run Chinook Salmon Juveniles at Chipps Trawl. Points indicate median fork length."}
chipps_gen <- read_csv("data_raw/chipps_genetic_data.csv")
chipps_lad <- chipps_gen %>%
  filter(LengthByDate == "Winter") %>%
  mutate(Race = LengthByDate, 
         RaceType = "LAD") 

chipps_genetic <- chipps_gen %>%
  filter(GeneticID == "Winter") %>%
  mutate(Race = GeneticID, 
         RaceType = "DNA") 

chipps_winter <- bind_rows(chipps_lad, chipps_genetic) %>%
  mutate(WY = if_else(month(SampleDate) > 9, year(SampleDate) + 1, year(SampleDate))) 

median_chipps_fl <- chipps_winter %>% group_by(WY, RaceType) %>%
  summarize(ForkLength = median(ForkLength))

ggplot() +
  geom_density_ridges(data = chipps_winter, aes(x = ForkLength, y = factor(WY), fill = RaceType), scale = 1.5, draw_baseline = FALSE) +
  geom_point(data = median_chipps_fl, aes(x = ForkLength, y = factor(WY)), shape = 21)+
  labs(x = 'Fork Length (mm)', y = 'Water Year') +
  facet_wrap(~RaceType) + 
  theme_bw() +
  theme(legend.position = 'none',
        plot.margin = ggplot2::margin(0.5,0.5,0.25,0.25, unit = 'cm'),
        axis.title.x = element_text(margin=ggplot2::margin(t=10)),
        axis.title.y = element_text(margin=ggplot2::margin(r=10)))
```

---

### Loss

```{r}
daily_salvage <- read_csv("data_raw/delta_loss.csv")

ggplotly(ggplot(daily_salvage) + 
  geom_line(aes(Date, cumLoss, color = Facility), size = 1.1) +
  geom_point(aes(Date, Expanded.Salvage, color = Facility), size = 0.9) + 
  scale_color_manual(values = c("blue", "goldenrod3"))+
  labs(y = "Cumulative Loss") + 
  theme_bw())
```

Winter-run Current and Historic Cumulative Salvage (Line plots)

```{r}

```

Current + Historic Percent of JPE

```{r}

```

Monitoring Sources for abundance, growth/size, migration timing/duration

-   Sac Trawl
-   Tisdale Weir
-   Knights Landing
-   GCID
-   DJFMP
-   Yolo Bypass
-   Chipps Island Trawl (Exit)
-   Genetic (Chipps, SWP/CVP, Knights Landing, Yolo Bypass)

1.  Abundance (Count) (IEP Monitoring)

2.  Condition (IEP Monitoring)

-   FL

3.  Migration Timing (IEP Monitoring)

-   SacPAS style plots of historical and current year?

*Chipps Trawl Timing*

*Sac Trawl Timing*

*Sac Beach Seine Timing*

4.  Migration Duration

-   Calfish Track/ERDDAP

5.  Migration Routing

6.  Survival

-   Hatchery real-time: Calfish Track/ERDDAP
-   Natural Origin Smolt survival (O Farell et al. 2018)
-   Hatchery Origin Smolt survival
-   Modeled: \*\* Juvenile: STARS \*\* Fish Model
-   Survival to Delta: Production (Hatchery JPE, Modeled JPE)
